### 2022-01-11 Report/Paper_OpenSet.tex
Added report template and notes

% CVPR 2022 Paper Template
% based on the CVPR template provided by Ming-Ming Cheng (https://github.com/MCG-NKU/CVPR_Template)
% modified and extended by Stefan Roth (stefan.roth@NOSPAMtu-darmstadt.de)

\documentclass[10pt,twocolumn,letterpaper]{article}

%%%%%%%%% PAPER TYPE  - PLEASE UPDATE FOR FINAL VERSION
%\usepackage[review]{cvpr}      % To produce the REVIEW version
\usepackage{cvpr}              % To produce the CAMERA-READY version
%\usepackage[pagenumbers]{cvpr} % To force page numbers, e.g. for an arXiv version

% Include other packages here, before hyperref.
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}

% It is strongly recommended to use hyperref, especially for the review version.
% hyperref with option pagebackref eases the reviewers' job.
% Please disable hyperref *only* if you encounter grave issues, e.g. with the
% file validation for the camera-ready version.
%
% If you comment hyperref and then uncomment it, you should delete
% ReviewTempalte.aux before re-running LaTeX.
% (Or just hit 'q' on the first LaTeX run, let it finish, and you
%  should be clear).
\usepackage[pagebackref,breaklinks,colorlinks]{hyperref}

% Support for easy cross-referencing
\usepackage[capitalize]{cleveref}
\crefname{section}{Sec.}{Secs.}
\Crefname{section}{Section}{Sections}
\Crefname{table}{Table}{Tables}
\crefname{table}{Tab.}{Tabs.}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{*****} % *** Enter the CVPR Paper ID here
\def\confName{CVPR}
\def\confYear{2022}

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{Open-Set Domain Adaptation through Self-Supervision}

\author{Daniele Rege Cambrin, Kylie Bedwell, Tommaso Natta, Ehsan Ansari Nejad\\
Politecnico di Torino\\
Corso Duca degli Abruzzi, 24\\
10129 Torino, ITALY\\
{\tt\small s290144@studenti.polito.it, s287581@studenti.polito.it} \\
{\tt\small s282478@studenti.polito.it, s288903@studenti.polito.it}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
   - sentence describing the problem
 - sentence describing our proposed method
 - sentence summarising the results
 - sentence about the variations
 - sentence about the variation results
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}
\label{sec:intro}

- Introduce the problem
- state our focus
- the network used
- the dataset used
- introduce the variations we will implement

%------------------------------------------------------------------------
\section{Related Work}
\label{sec:relatedWork}

- what's been done in the past on this topic
 - Summarise each of the cited references
- Cite some papers about the variations we did
 - other variations which might be interesting (but that we didnt do) - if space
-

%------------------------------------------------------------------------
\section{Method}
\label{sec:method}

- describe in detail the method used
- include the diagrams here and explain them
- explain the evaluation parameters that will be used

%------------------------------------------------------------------------
\section{Experiments}
\label{sec:experiments}

- start with parameter tuning of learning rate and epochs, include graph to justify decision
- ablation study: hyperparameter tuning of weights and threshold value, include graphs or tables of values

%------------------------------------------------------------------------
\section{Variations}
\label{sec:variations}

- describe each of the variations
- present results of the performance of the model and compare with the baseline for each of the variations

%------------------------------------------------------------------------
\section{Conclusions}
\label{sec:conclusion}

- summarise the results
- add future recommendations

\subsection{Acknowledgements}
The authors would like to thank Silvia Bucci for her assistance and guidance in completing this study.

%%%%%%%%% REFERENCES
{\small
\bibliographystyle{ieee_fullname}
%\bibliography{egbib}
}

\end{document}

### 2022-01-11 dataset.py
fix boolean labels

@@ -117,10 +117,10 @@ class FlipDataset(data.Dataset):
             img = self.image_transformer(img)
 
         
-        # produce a random label True or False
-        flip_flag = True if random.randrange(2) == 0 else False
-        # The angles of rotation are 0°, 90°, 180°, 270° that correspond to labels 0, 1, 2, 3.
-        if flip_flag == True:
+        # produce a random label 1 (True) or 0 (False)
+        flip_flag = random.randrange(2)
+        # image is either flipped or not that correspond to labels 0, 1.
+        if flip_flag == 1:
             img_flip = torch.fliplr(img)
         else: 
             img_flip = img
@@ -151,10 +151,10 @@ class TestFlipDataset(data.Dataset):
             img = self.image_transformer(img)
 
         
-        # produce a random label True or False
-        flip_flag = True if random.randrange(2) == 0 else False
-        # The angles of rotation are 0°, 90°, 180°, 270° that correspond to labels 0, 1, 2, 3.
-        if flip_flag == True:
+        # produce a random label 1 (True) or 0 (False)
+        flip_flag = random.randrange(2)
+        # image is either flipped or not that correspond to labels 0, 1.
+        if flip_flag == 1:
             img_flip = torch.fliplr(img)
         else: 
             img_flip = img

### 2022-01-11 step2_SourceTargetAdapt.py
Output files for learning rate tuning

@@ -217,7 +217,8 @@ def step2(
         args.train_all,
     )
 
-    for _ in range(args.epochs_step2):
+    for epoch in range(args.epochs_step2):
+        print("Epoch: ", epoch)
         _do_epoch(
             args,
             feature_extractor,

### 2022-01-11 eval_target.py
eval and classifier adapted to hf

@@ -66,11 +66,21 @@ def evaluation(
             )
             original_features = feature_extractor(data)
 
+            """
             entropy_losses = torch.zeros([4])
             rotation_scores = torch.zeros([4, 4])
             for i in range(1, 5):
+            
                 rotated_features = feature_extractor(
                     torch.rot90(data, k=i, dims=[2, 3])
+                )
+            """
+            entropy_losses = torch.zeros([2])
+            rotation_scores = torch.zeros([2, 2])
+            for i in range(1, 3):
+            
+                rotated_features = feature_extractor(
+                    torch.fliplr(data) if i==1 else data
                 )
                 rotation_probabilities = torch.nn.Softmax(dim=0)(
                     torch.flatten(

### 2022-01-11 main.py

@@ -168,8 +168,12 @@ class Trainer:
         self.feature_extractor = resnet18_feat_extractor()
         # Initiate object classifier with input_size=512, and numbers of classes is known classes + 1 (the unknown class, trained only in step2)
         self.obj_classifier = Classifier(512, self.args.n_classes_known + 1)
-        # Initiate rotation classifier with input_size=512*2 and 4 classes: [0, 90, 180, 270]
-        self.rot_classifier = Classifier(512 * 2, 4)
+        if args.variation == "horizontal_flipping":
+            # Initiate flipping classifier with input_size=512*2 and 2 classes: [flipped, not flipped]
+            self.rot_classifier = Classifier(512 * 2 , 2)
+        else:
+            # Initiate rotation classifier with input_size=512*2 and 4 classes: [0, 90, 180, 270]
+            self.rot_classifier = Classifier(512 * 2, 4)
 
         if args.load_weights:
             self.rot_classifier.load_state_dict(

### 2022-01-12 main.py
align to development

@@ -274,6 +274,8 @@ class Trainer:
                 self.device,
             )
 
+            print("<------End")
+
 
 def main():
     # main function of the program

### 2022-01-12 step2_SourceTargetAdapt.py

@@ -113,7 +113,7 @@ def _do_epoch(
 
     # compute accuracy on class and rotation predictions
     acc_cls = correct_classes / len(source_loader.dataset)
-    acc_rot = correct_rotations / len(target_loader_train.dataset)
+    acc_rot = correct_rotations / len(source_loader.dataset)
 
     print(
         "Class Loss %.4f, Class Accuracy %.4f,Rot Loss %.4f, Rot Accuracy %.4f"
@@ -217,7 +217,8 @@ def step2(
         args.train_all,
     )
 
-    for _ in range(args.epochs_step2):
+    for epoch in range(args.epochs_step2):
+        print("Epoch: ", epoch)
         _do_epoch(
             args,
             feature_extractor,

### 2022-01-12 Report/Paper_OpenSet.tex

@@
 
+In the computer vision research area large amounts of unlabeled data are available, however the cost of labelling this data is high ~\cite{Csurka2017}.
+Domain adaptation is one technique that can be used to exploit the unlabeled data by first training a model on labeled data from a different but similar domain (the \textit{source} domain), and then applying this model to the unlabeled data ( the \textit{target} domain).
+This technique assumes the distribution of both source and target domans are similar and describe the same class labels, also known as the \textit{closed-set} scenario~\cite{Bucci2020}.
+When applied to real-word scenarios however it is possible that the target domain includes previously unseen classes, known as the \textit{open-set} scenario.
+These extra class labels in the target domain will cause performance degradation of the classification model and should be identified and isolated.
+The problem thus consists of two steps: first separating the target domain into known and unknown samples; then conducting domain alignment between the source domain and the known samples of the target domain.
+
+Self-supervised learning can be used to separate the known class samples in the target domain from the unknown samples. Self-supervised learning involves using known ...
+
 - Introduce the problem
@@
 \bibliographystyle{ieee_fullname}
-%\bibliography{egbib}
+\bibliography{egbib}
 }

### 2022-01-12 data_helper.py
remove arg

@@ -2,7 +2,7 @@ import torch
 import torch.utils.data as data
 from torchvision import transforms
 
-from dataset import Dataset, TestDataset, FlipDataset, TestFlipDataset, _dataset_info
+from dataset import FlipDataset, TestFlipDataset, _dataset_info
 
 """
 get_train_dataloader(args,txt_file) 
@@ -37,14 +37,9 @@ def get_train_dataloader(args, txt_file):
 
     img_transformer = get_train_transformers(args)
     name_train, labels_train = _dataset_info(txt_file)
-    if args.variation == "horizontal_flipping":
-        train_dataset = FlipDataset(
-            name_train, labels_train, args.path_dataset, img_transformer=img_transformer
-        )
-    else: #else if args.variation == "rotation":
-        train_dataset = Dataset(
-            name_train, labels_train, args.path_dataset, img_transformer=img_transformer
-        )   
+    train_dataset = FlipDataset(
+        name_train, labels_train, args.path_dataset, img_transformer=img_transformer
+    )
     
     
     loader = torch.utils.data.DataLoader(
@@ -64,10 +59,8 @@ def get_val_dataloader(args, txt_file):
 
     names, labels = _dataset_info(txt_file)
     img_tr = get_test_transformer(args)
-    if args.variation == "horizontal_flipping":
-        test_dataset = TestFlipDataset(names, labels, args.path_dataset, img_transformer=img_tr)
-    else: #else if args.variation == "rotation":
-        test_dataset = TestDataset(names, labels, args.path_dataset, img_transformer=img_tr)
+    
+    test_dataset = TestFlipDataset(names, labels, args.path_dataset, img_transformer=img_tr)
     loader = torch.utils.data.DataLoader(
         test_dataset,
         batch_size=1,

### 2022-01-12 dataset.py

@@ -21,81 +21,6 @@ def _dataset_info(txt_labels) -> Tuple[List[str], List[int]]:
 
     return file_names, labels
 
-
-# It returns train_dataset
-class Dataset(data.Dataset):
-    def __init__(
-        self,
-        names: List[str],
-        labels: List[int],
-        path_dataset: str,
-        img_transformer: Optional[transforms.Compose] = None,
-    ):
-        self.data_path = path_dataset
-        self.names = names
-        self.labels = labels
-        self.image_transformer = img_transformer
-
-    def __getitem__(self, index: int) -> Tuple[torch.Tensor, int, torch.Tensor, int]:
-        # Get and process image
-        image_path = self.data_path + "/" + self.names[index]
-        img = Image.open(image_path).convert("RGB")
-        if self.image_transformer:
-            img = self.image_transformer(img)
-        # produce a random label between 0,1,2,3
-        index_rot = random.randrange(4)
-        # The angles of rotation are 0°, 90°, 180°, 270° that correspond to labels 0, 1, 2, 3.
-        if index_rot == 0:
-            img_rot = img
-        elif index_rot == 1:
-            img_rot = torch.rot90(img, k=1, dims=[1, 2])
-        elif index_rot == 2:
-            img_rot = torch.rot90(img, k=2, dims=[1, 2])
-        elif index_rot == 3:
-            img_rot = torch.rot90(img, k=3, dims=[1, 2])
-
-        return img, self.labels[index], img_rot, index_rot
-
-    def __len__(self):
-        return len(self.names)
-
-
-# It returns test_dataset
-class TestDataset(data.Dataset):
-    def __init__(
-        self,
-        names: List[str],
-        labels: List[int],
-        path_dataset: str,
-        img_transformer: Optional[transforms.Compose] = None,
-    ):
-        self.data_path = path_dataset
-        self.names = names
-        self.labels = labels
-        self.image_transformer = img_transformer
-
-    def __getitem__(self, index: int) -> Tuple[torch.Tensor, int, torch.Tensor, int]:
-        image_path = self.data_path + "/" + self.names[index]
-        img = Image.open(image_path).convert("RGB")
-        if self.image_transformer:
-            img = self.image_transformer(img)
-        # produce a random label between 0,1,2,3
-        index_rot = random.randrange(4)
[…]

### 2022-01-12 main.py

@@ -131,15 +131,6 @@ def get_args():
         help="Choose steps to run",
     )
 
-    parser.add_argument(
-        "--variation",
-        type=str,
-        default="rotation",
-        choices=["rotation",  "horizontal_flipping", "jigsaw_puzzle"
-        #,"odd_one_out", "translations" #not implemented
-        ],
-        help="Number of epochs of step1 for known/unknown separation",
-    )
 
     return parser.parse_args()
 
@@ -168,12 +159,8 @@ class Trainer:
         self.feature_extractor = resnet18_feat_extractor()
         # Initiate object classifier with input_size=512, and numbers of classes is known classes + 1 (the unknown class, trained only in step2)
         self.obj_classifier = Classifier(512, self.args.n_classes_known + 1)
-        if args.variation == "horizontal_flipping":
-            # Initiate flipping classifier with input_size=512*2 and 2 classes: [flipped, not flipped]
-            self.rot_classifier = Classifier(512 * 2 , 2)
-        else:
-            # Initiate rotation classifier with input_size=512*2 and 4 classes: [0, 90, 180, 270]
-            self.rot_classifier = Classifier(512 * 2, 4)
+        # Initiate flipping classifier with input_size=512*2 and 2 classes: [flipped, not flipped]
+        self.rot_classifier = Classifier(512 * 2 , 2)
 
         if args.load_weights:
             self.rot_classifier.load_state_dict(

### 2022-01-12 eval_target.py
debug files

@@ -138,7 +138,7 @@ def evaluation(
                 number_of_known_samples += 1
             else:
                 # we consider the domain of the image as UNknown
-                target_unknown.write(f"{target_loader_eval.dataset.names[img_id]} 45\n")
+                target_unknown.write(f"{target_loader_eval.dataset.names[img_id]} {args.n_classes_known}\n")
                 number_of_unknown_samples += 1
 
     target_known.close()

### 2022-01-12 eval_target.py
print statements

@@ -125,6 +125,7 @@ def evaluation(
 
     number_of_known_samples = 0
     number_of_unknown_samples = 0
+    print("treshold: " + args.treshold)
     with torch.no_grad():
         for img_id, (_, class_l, _, _) in enumerate(target_loader_eval):
             # DEBUG VERSION
@@ -132,6 +133,9 @@ def evaluation(
             #    break
             if normality_score[img_id] >= args.threshold:
                 # we consider the domain of the image as known
+                print(img_id)
+                print(normality_score[img_id])
+                print()
                 target_known.write(
                     f"{target_loader_eval.dataset.names[img_id]} {class_l.item()}\n"
                 )

### 2022-01-12 eval_target.py
mispelling

@@ -125,7 +125,7 @@ def evaluation(
 
     number_of_known_samples = 0
     number_of_unknown_samples = 0
-    print("treshold: " + args.treshold)
+    print("treshold: " + args.threshold)
     with torch.no_grad():
         for img_id, (_, class_l, _, _) in enumerate(target_loader_eval):
             # DEBUG VERSION

### 2022-01-12 eval_target.py
printing

@@ -125,7 +125,7 @@ def evaluation(
 
     number_of_known_samples = 0
     number_of_unknown_samples = 0
-    print("treshold: " + args.threshold)
+    print("treshold: " + str(args.threshold))
     with torch.no_grad():
         for img_id, (_, class_l, _, _) in enumerate(target_loader_eval):
             # DEBUG VERSION

### 2022-01-12 step2_SourceTargetAdapt.py
Step2 accuracies are coputed correctly (probably)

@@ -148,11 +148,9 @@ def _do_epoch(
             class_prediction = torch.argmax(class_scores, dim=1)
 
             # Update counters
-            if class_label == args.n_classes_known:
+            if class_label >= args.n_classes_known:
                 total_classes_unknown += 1
-                correct_classes_unknown += torch.sum(
-                    class_prediction == class_label
-                ).item()
+                correct_classes_unknown += torch.sum(class_prediction == 45).item()
             else:
                 total_classes_known += 1
                 correct_classes_known += torch.sum(

### 2022-01-12 data_helper.py
print statements

@@ -36,6 +36,7 @@ def get_train_dataloader(args, txt_file):
     """
 
     img_transformer = get_train_transformers(args)
+    print("\nReading: " + txt_file)
     name_train, labels_train = _dataset_info(txt_file)
     train_dataset = FlipDataset(
         name_train, labels_train, args.path_dataset, img_transformer=img_transformer

### 2022-01-12 dataset.py

@@ -15,8 +15,11 @@ def _dataset_info(txt_labels) -> Tuple[List[str], List[int]]:
     file_names = []
     labels = []
     for row in images_list:
+        print()
         row = row.split(" ")
+        print(row[0])
         file_names.append(row[0])
+        print(row[1])
         labels.append(int(row[1]))
 
     return file_names, labels

### 2022-01-12 eval_target.py
fix source_unknown file writing and remove debug prints

@@ -119,13 +119,14 @@ def evaluation(
         f"new_txt_list/{args.source}_known_{rand}.txt",
     )
     target_unknown = open(source_unknown_path, "a+")
+    #new line at the end of source images, otherwise first target unknown image is on the same line as last source image
+    target_unknown.write(f"\n")
 
     # This txt files will have the names of the target images selected as known
     target_known = open(f"new_txt_list/{args.target}_known_{rand}.txt", "w+")
 
     number_of_known_samples = 0
     number_of_unknown_samples = 0
-    print("treshold: " + str(args.threshold))
     with torch.no_grad():
         for img_id, (_, class_l, _, _) in enumerate(target_loader_eval):
             # DEBUG VERSION
@@ -133,9 +134,6 @@ def evaluation(
             #    break
             if normality_score[img_id] >= args.threshold:
                 # we consider the domain of the image as known
-                print(img_id)
-                print(normality_score[img_id])
-                print()
                 target_known.write(
                     f"{target_loader_eval.dataset.names[img_id]} {class_l.item()}\n"
                 )

### 2022-01-12 data_helper.py
remove backslash Art file, step2 debug prints

@@ -36,7 +36,6 @@ def get_train_dataloader(args, txt_file):
     """
 
     img_transformer = get_train_transformers(args)
-    print("\nReading: " + txt_file)
     name_train, labels_train = _dataset_info(txt_file)
     train_dataset = FlipDataset(
         name_train, labels_train, args.path_dataset, img_transformer=img_transformer

### 2022-01-12 dataset.py

@@ -15,11 +15,8 @@ def _dataset_info(txt_labels) -> Tuple[List[str], List[int]]:
     file_names = []
     labels = []
     for row in images_list:
-        print()
         row = row.split(" ")
-        print(row[0])
         file_names.append(row[0])
-        print(row[1])
         labels.append(int(row[1]))
 
     return file_names, labels

### 2022-01-12 main.py

@@ -244,6 +244,7 @@ class Trainer:
             self.target_loader_train = data_helper.get_train_dataloader(
                 self.args, target_path_file
             )
+            print("Reading target path file: " + target_path_file)
             self.target_loader_eval = data_helper.get_val_dataloader(
                 self.args, target_path_file
             )

### 2022-01-12 step2_SourceTargetAdapt.py

@@ -130,7 +130,9 @@ def _do_epoch(
     correct_classes_unknown = 0
     total_classes_known = 0
     total_classes_unknown = 0
-
+    
+    print("Number of known classes: ")
+    print(args.n_classes_known)
     # deactivate autograd engine for speedup during evaluation phase
     with torch.no_grad():
         for it, (data, class_label, _, _) in enumerate(target_loader_eval):
@@ -146,7 +148,10 @@ def _do_epoch(
 
             # Get predictions
             class_prediction = torch.argmax(class_scores, dim=1)
-
+            
+            print()
+            print(class_label)
+            
             # Update counters
             if class_label == args.n_classes_known:
                 total_classes_unknown += 1

### 2022-01-12 step2_SourceTargetAdapt.py
additional step2 debug prints

@@ -151,7 +151,7 @@ def _do_epoch(
             
             print()
             print(class_label)
-            
+
             # Update counters
             if class_label == args.n_classes_known:
                 total_classes_unknown += 1
@@ -163,6 +163,11 @@ def _do_epoch(
                 correct_classes_known += torch.sum(
                     class_prediction == class_label
                 ).item()
+
+        print("\n\ntotal classes known: " + str(total_classes_known))
+        print("total classes unknown: " + str(total_classes_unknown))
+        print("correct classes unknown: " + str(correct_classes_known))
+        print("correct classes unknown: " + str(correct_classes_unknown))
 
         # compute accuracies
         if total_classes_unknown == 0:

### 2022-01-12 step2_SourceTargetAdapt.py
step2 debug prints

@@ -151,6 +151,8 @@ def _do_epoch(
             
             print()
             print(class_label)
+            print(class_prediction)
+            print(class_scores)
 
             # Update counters
             if class_label == args.n_classes_known:

### 2022-01-12 step2_SourceTargetAdapt.py
decrease debug prints for big test

@@ -148,12 +148,12 @@ def _do_epoch(
 
             # Get predictions
             class_prediction = torch.argmax(class_scores, dim=1)
-            
+            """
             print()
             print(class_label)
             print(class_prediction)
             print(class_scores)
-
+            """
             # Update counters
             if class_label == args.n_classes_known:
                 total_classes_unknown += 1

### 2022-01-12 step2_SourceTargetAdapt.py
typo fix

@@ -168,7 +168,7 @@ def _do_epoch(
 
         print("\n\ntotal classes known: " + str(total_classes_known))
         print("total classes unknown: " + str(total_classes_unknown))
-        print("correct classes unknown: " + str(correct_classes_known))
+        print("correct classes known: " + str(correct_classes_known))
         print("correct classes unknown: " + str(correct_classes_unknown))
 
         # compute accuracies

### 2022-01-13 step1_KnownUnknownSep.py
change rot to flip in prints, remove debug prints

@@ -123,7 +123,7 @@ def step1(
             args, feature_extractor, rot_cls, obj_cls, source_loader, optimizer, device
         )
         print(
-            "Class Loss %.4f, Class Accuracy %.4f,Rot Loss %.4f, Rot Accuracy %.4f"
+            "Class Loss %.4f, Class Accuracy %.4f,Flip Loss %.4f, Flip Accuracy %.4f"
             % (class_loss, acc_cls, rot_loss, acc_rot)
         )
         if epoch % 10 == 0:

### 2022-01-13 step2_SourceTargetAdapt.py

@@ -116,7 +116,7 @@ def _do_epoch(
     acc_rot = correct_rotations / len(source_loader.dataset)
 
     print(
-        "Class Loss %.4f, Class Accuracy %.4f,Rot Loss %.4f, Rot Accuracy %.4f"
+        "Class Loss %.4f, Class Accuracy %.4f,Flip Loss %.4f, Flip Accuracy %.4f"
         % (class_loss.item(), acc_cls, rot_loss.item(), acc_rot)
     )
 
@@ -131,8 +131,6 @@ def _do_epoch(
     total_classes_known = 0
     total_classes_unknown = 0
     
-    print("Number of known classes: ")
-    print(args.n_classes_known)
     # deactivate autograd engine for speedup during evaluation phase
     with torch.no_grad():
         for it, (data, class_label, _, _) in enumerate(target_loader_eval):

### 2022-01-13 step2_SourceTargetAdapt.py
alight to development - step2 classes unknown

@@ -153,10 +153,10 @@ def _do_epoch(
             print(class_scores)
             """
             # Update counters
-            if class_label == args.n_classes_known:
+            if class_label >= args.n_classes_known:
                 total_classes_unknown += 1
                 correct_classes_unknown += torch.sum(
-                    class_prediction == class_label
+                    class_prediction == args.n_classes_known
                 ).item()
             else:
                 total_classes_known += 1

### 2022-01-13 eval_target.py
change hardcoded value 45 to args.n_classes_known

@@ -128,7 +128,7 @@ def evaluation(
                 number_of_known_samples += 1
             else:
                 # we consider the domain of the image as UNknown
-                target_unknown.write(f"{target_loader_eval.dataset.names[img_id]} 45\n")
+                target_unknown.write(f"{target_loader_eval.dataset.names[img_id]} {args.n_classes_known}\n")
                 number_of_unknown_samples += 1
 
     target_known.close()

### 2022-01-13 step2_SourceTargetAdapt.py

@@ -150,7 +150,7 @@ def _do_epoch(
             # Update counters
             if class_label >= args.n_classes_known:
                 total_classes_unknown += 1
-                correct_classes_unknown += torch.sum(class_prediction == 45).item()
+                correct_classes_unknown += torch.sum(class_prediction == args.n_classes_known).item()
             else:
                 total_classes_known += 1
                 correct_classes_known += torch.sum(

### 2022-01-13 eval_target.py
added debug mode and corrected new line error in eval

@@ -109,7 +109,9 @@ def evaluation(
         f"new_txt_list/{args.source}_known_{rand}.txt",
     )
     target_unknown = open(source_unknown_path, "a+")
-
+    #new line at the end of source images, otherwise first target unknown image is on the same line as last source image
+    target_unknown.write(f"\n")
+    
     # This txt files will have the names of the target images selected as known
     target_known = open(f"new_txt_list/{args.target}_known_{rand}.txt", "w+")
 

### 2022-01-14 Report/Paper_OpenSet.tex
Finished introduction

@@
 
-In the computer vision research area large amounts of unlabeled data are available, however the cost of labelling this data is high ~\cite{Csurka2017}.
+In the computer vision research area large amounts of unlabeled data are available, however the cost of labeling this data is high ~\cite{Csurka2017}.
 Domain adaptation is one technique that can be used to exploit the unlabeled data by first training a model on labeled data from a different but similar domain (the \textit{source} domain), and then applying this model to the unlabeled data ( the \textit{target} domain).
-This technique assumes the distribution of both source and target domans are similar and describe the same class labels, also known as the \textit{closed-set} scenario~\cite{Bucci2020}.
+This technique assumes the distribution of both source and target domains are similar and describe the same class labels, also known as the \textit{closed-set} scenario~\cite{Bucci2020}.
 When applied to real-word scenarios however it is possible that the target domain includes previously unseen classes, known as the \textit{open-set} scenario.
@@
 
-Self-supervised learning can be used to separate the known class samples in the target domain from the unknown samples. Self-supervised learning involves using known ...
+Self-supervised learning can be used to separate the known class samples in the target domain from the unknown samples.
+Self-supervised learning involves the transformation of data using a known transform (for example by using image rotation), then training a model to predict the transformation~\cite{Xu2019}.
+When used in an object classification task and considering the image rotation transformation, the correct orientation of an object is domain-invariant.
+In this way the model can be trained to predict the correct orientation of the image using data from the source domain, then applied to the images of the target domain.
+If the orientation of a sample in the target domain is predicted correctly then it is considered to be of a \textit{known} class.
+Contrarily if the orientation is not prediction correctly it is labelled as \textit{unknown}.
 
-- Introduce the problem
-- state our focus
-- the network used
-- the dataset used
-- introduce the variations we will implement
+Domain adaptation can then be performed between the samples in the source domain and the samples recognized as known in the target domain.
+When applying domain adaptation to an open-set scenario (Open-Set Domain Adapatation or OSDA) the samples classified as unknown can be treated as a separate class and incorporated into the Closed-Set Domain Adaptation (CSDA) task~\cite{Pau2020}.
+The self-supervised rotation task can also be used to reduce the domain shift during this step, using the Rotation-based Open Set (ROS) method developed by Bucci \etal \cite{Bucci2020}.
+
+This study investigates the use of a simplified ROS method for object classification on the \textit{Office-Home} dataset \cite{OfficeHome}.
+Alternative self-supervised tasks \textcolor{red}{as well as the inclusion of center-loss} are also considered and their performance on the object classification task is evaluated.
 
@@
 - describe in detail the method used
+- the network used
 - include the diagrams here and explain them

### 2022-01-14 Report/Paper_OpenSet.tex
Related Work - Anomaly detection

@@
 
+\textbf{Anomaly detection}, or outlier/novelty detection, in an open-set scenario can be used to detect samples belonging to the unknown or unseen class.
+Various different approaches for anomaly detection have been used in the literature as applied to the open-set scenario.
+Golan and El-Yanic \cite{Golan2018} present a method for using geometric transformations to create a self-labeled dataset.
+In this way the neural classifier learns features that are effective for the detection of anomalies.
+Sakurada and Yairi \cite{Sakurada2014} on the other hand make use of autoencoders with dimensionality reduction.
+This method assumes the data have correlations that can clearly separate normal and anomalous samples when reduced to a lower dimensional subspace.
+After the test data is projected into the subspace it is then reconstructed and the corresponding reconstruction error is used to identify the anomalous samples.
+
+\textcolor{red}{Not sure if the Sakurada study is relevant to our work}
+
+\textbf{Self-supervised learning}...
+\cite{Xu2019}, Komodakis,
+
+\textbf{Domain adaptation} ...
+Calucci, Csurka, Pau
+
+\textbf{Rotation-based Open Set}...
+\cite{Bucci2020}
+
 - what's been done in the past on this topic

### 2022-01-14 Report/Paper_OpenSet.tex
Related Work - Self-supervised learning

@@
 
-\textcolor{red}{Not sure if the Sakurada study is relevant to our work}
-
-\textbf{Self-supervised learning}...
-\cite{Xu2019}, Komodakis,
+\textbf{Self-supervised learning} has been a key concept aimed at reducing the need for human labeling of data.
+It has also created opportunities for the use of data in problems where supervision is not possible \cite{Yaman2020}.
+Self-supervised learning consists of choosing a self-supervised task (or pretext task) to train alongside the main classification task.
+One possible self-supervised task is image rotation prediction, which is reported to perform best for visual representation learning \cite{Xu2019, Gidaris2018}.
+However many options are available, including image-patch based methods \cite{Mundhenk2018, Kim2018}, horizontal flipping \cite{Golan2018}, or by solving jigsaw puzzles \cite{Carlucci2019, Kim2018}.
 
 \textbf{Domain adaptation} ...
-Calucci, Csurka, Pau
+Calucci, Csurka, Pau, Zhang2016, Ren2021
 
 \textbf{Rotation-based Open Set}...
-\cite{Bucci2020}
-
-- what's been done in the past on this topic
- - Summarise each of the cited references
-- Cite some papers about the variations we did
- - other variations which might be interesting (but that we didnt do) - if space
--
+\cite{Bucci2020}, center-loss paper
 

### 2022-01-15 eval_target.py
Some weights (not too much improvement) and improved normality score

@@ -67,7 +67,7 @@ def evaluation(
             original_features = feature_extractor(data)
 
             entropy_losses = torch.zeros([4])
-            rotation_scores = torch.zeros([4, 4])
+            rotation_scores = torch.zeros([4])
             for i in range(1, 5):
                 rotated_features = feature_extractor(
                     torch.rot90(data, k=i, dims=[2, 3])
@@ -81,9 +81,8 @@ def evaluation(
                     rotation_probabilities.dot(torch.log10(rotation_probabilities))
                     / log(args.n_classes_known, 10)
                 ).item()
-                rotation_scores[i - 1] = rotation_probabilities
-            # normality score is maximum prediction of a class. e.g. if image is rotated 90° left with 70% probability, normality score = 0.7
-            normality_score[index] = torch.max(torch.mean(rotation_scores, dim=0))
+                rotation_scores[i - 1] = rotation_probabilities[i - 1]
+            normality_score[index] = torch.max(rotation_scores)
             """If you want to use entropy
             normality_score[index] = torch.max(
                 normality_score[index], 1 - torch.mean(entropy_losses)
@@ -109,9 +108,9 @@ def evaluation(
         f"new_txt_list/{args.source}_known_{rand}.txt",
     )
     target_unknown = open(source_unknown_path, "a+")
-    #new line at the end of source images, otherwise first target unknown image is on the same line as last source image
+    # new line at the end of source images, otherwise first target unknown image is on the same line as last source image
     target_unknown.write(f"\n")
-    
+
     # This txt files will have the names of the target images selected as known
     target_known = open(f"new_txt_list/{args.target}_known_{rand}.txt", "w+")
 
@@ -130,7 +129,9 @@ def evaluation(
                 number_of_known_samples += 1
             else:
                 # we consider the domain of the image as UNknown
-                target_unknown.write(f"{target_loader_eval.dataset.names[img_id]} {args.n_classes_known}\n")
+                target_unknown.write(
+                    f"{target_loader_eval.dataset.names[img_id]} {args.n_classes_known}\n"
+                )
                 number_of_unknown_samples += 1
 
     target_known.close()

### 2022-01-16 eval_target.py
Find out the stupid error (La notte porta consiglio)

@@ -68,20 +68,21 @@ def evaluation(
 
             entropy_losses = torch.zeros([4])
             rotation_scores = torch.zeros([4])
-            for i in range(1, 5):
-                rotated_features = feature_extractor(
-                    torch.rot90(data, k=i, dims=[2, 3])
-                )
+            for i in range(4):
+                rotated = torch.rot90(data, k=i, dims=[2, 3])
+                rotated_features = feature_extractor(rotated)
                 rotation_probabilities = torch.nn.Softmax(dim=0)(
                     torch.flatten(
                         rot_cls(torch.cat([original_features, rotated_features], 1))
                     )
                 )
-                entropy_losses[i - 1] = (
+                entropy_losses[i] = (
                     rotation_probabilities.dot(torch.log10(rotation_probabilities))
                     / log(args.n_classes_known, 10)
                 ).item()
-                rotation_scores[i - 1] = rotation_probabilities[i - 1]
+                rotation_scores[i] = rotation_probabilities[i]
+
+            # normality score is maximum prediction of a class. e.g. if image is rotated 90° left with 70% probability, normality score = 0.7
             normality_score[index] = torch.max(rotation_scores)
             """If you want to use entropy
             normality_score[index] = torch.max(

### 2022-01-17 eval_target.py
align to development

@@ -77,21 +77,19 @@ def evaluation(
             """
             entropy_losses = torch.zeros([2])
             rotation_scores = torch.zeros([2, 2])
-            for i in range(1, 3):
-            
-                rotated_features = feature_extractor(
-                    torch.fliplr(data) if i==1 else data
-                )
+            for i in range(2):
+                flipped = torch.fliplr(data) if i==1 else data
+                rotated_features = feature_extractor(flipped)
                 rotation_probabilities = torch.nn.Softmax(dim=0)(
                     torch.flatten(
                         rot_cls(torch.cat([original_features, rotated_features], 1))
                     )
                 )
-                entropy_losses[i - 1] = (
+                entropy_losses[i] = (
                     rotation_probabilities.dot(torch.log10(rotation_probabilities))
                     / log(args.n_classes_known, 10)
                 ).item()
-                rotation_scores[i - 1] = rotation_probabilities
+                rotation_scores[i] = rotation_probabilities
             # normality score is maximum prediction of a class. e.g. if image is rotated 90° left with 70% probability, normality score = 0.7
             normality_score[index] = torch.max(torch.mean(rotation_scores, dim=0))
             """If you want to use entropy

### 2022-01-17 Report/Paper_OpenSet.tex
Related Work - Domain adaptation

@@
 
-In the computer vision research area large amounts of unlabeled data are available, however the cost of labeling this data is high ~\cite{Csurka2017}.
+In the computer vision research area large amounts of unlabeled data are available, however the cost of labeling this data is high ~\cite{Csurka2017, Zhang2016}.
 Domain adaptation is one technique that can be used to exploit the unlabeled data by first training a model on labeled data from a different but similar domain (the \textit{source} domain), and then applying this model to the unlabeled data ( the \textit{target} domain).
@@
 
-\textbf{Domain adaptation} ...
-Calucci, Csurka, Pau, Zhang2016, Ren2021
+\textbf{Domain adaptation} techniques have advanced significantly in recent years for the closed-set scenario \cite{Pau2020}, however for real-world applications the closed-set assumption is often not applicable \cite{Ren2021}.
+It has become increasingly important to develop robust techniques for open-set domain adaptation to address this problem.
+Recent studies in this field include: the development of a generic approach to learn a linear mapping between the features of the source domain and target domain \cite{Pau2020}; the use of self-supervision to improve the generalization of models to different domains \cite{Carlucci2019}; or considering partial domain adaptation by using a discrepancy criterion to partially align features whilst avoiding negative transfer \cite{Ren2021}.
+These techniques have been reported to perform well, and increase the applicability of domain adaptation methods to real-world applications \cite{Carlucci2019, Ren2021,Pau2020}.
 
-\textbf{Rotation-based Open Set}...
+\textbf{Rotation-based Open Set} (ROS) is a specific technique developed by Bucci \etal \cite{Bucci2020} for open-set domain adaptation.
+
 \cite{Bucci2020}, center-loss paper
@@
 
-- start with parameter tuning of learning rate and epochs, include graph to justify decision
 - ablation study: hyperparameter tuning of weights and threshold value, include graphs or tables of values

### 2022-01-17 Report/Paper_OpenSet.tex
Related Work - ROS

@@
 It has become increasingly important to develop robust techniques for open-set domain adaptation to address this problem.
-Recent studies in this field include: the development of a generic approach to learn a linear mapping between the features of the source domain and target domain \cite{Pau2020}; the use of self-supervision to improve the generalization of models to different domains \cite{Carlucci2019}; or considering partial domain adaptation by using a discrepancy criterion to partially align features whilst avoiding negative transfer \cite{Ren2021}.
+Recent studies in this field include: the development of a generic approach to learn a linear mapping between the features of the source domain and target domain \cite{Pau2020}; the use of self-supervision to improve the generalization of models to different domains \cite{Carlucci2019}; partial domain adaptation by using a discrepancy criterion to partially align features whilst avoiding negative transfer \cite{Ren2021}.
 These techniques have been reported to perform well, and increase the applicability of domain adaptation methods to real-world applications \cite{Carlucci2019, Ren2021,Pau2020}.
 
-\textbf{Rotation-based Open Set} (ROS) is a specific technique developed by Bucci \etal \cite{Bucci2020} for open-set domain adaptation.
-
-\cite{Bucci2020}, center-loss paper
+\textbf{Rotation-based Open Set} (ROS) is a specific technique developed by Bucci \etal \cite{Bucci2020}.
+ROS is a two-stage method for open-set domain adaptation.
+The first stage separates samples in the target domain into known and unknown categories by training the model on a multi-rotation recognition task.
+The rotation recognition task includes the use of the center-loss to improve performance by learning a center of the features and minimizing the distances between features and their corresponding centers \cite{Wen2016}.
+The second stage conducts domain alignment, training both semantic and rotation classifiers to classify known target samples.
+Bucci \etal \cite{Bucci2020} also propose the use of the harmonic mean of the average class accuracies  for the known and unknown classes as a more robust and balanced evaluation metric.
 
@@
 \label{sec:method}
+
+ROS but without the center-loss and only a single-head rotation classifier.
 

### 2022-01-17 dataset.py
Update dataset.py

@@ -1,97 +1,171 @@
-import random
-from typing import List, Optional, Tuple
-
-import torch
 import torch.utils.data as data
-import torchvision.transforms as transforms
 from PIL import Image
+from random import random
+import random
+import torchvision
+import torchvision.transforms.functional as TF
+import torch
+import numpy as np
+import matplotlib.pyplot as plt
+from typing import List, Optional
+import torchvision.transforms as transforms
 
 
-def _dataset_info(txt_labels) -> Tuple[List[str], List[int]]:
-    """It will be used in data_helper to retrieve sample's name and associated label."""
-    with open(txt_labels, "r") as f:
+def _dataset_info(txt_labels):
+    with open(txt_labels, 'r') as f:
         images_list = f.readlines()
 
     file_names = []
     labels = []
     for row in images_list:
-        row = row.split(" ")
+        row = row.split(' ')
         file_names.append(row[0])
         labels.append(int(row[1]))
 
     return file_names, labels
 
 
-# It returns train_dataset
-class Dataset(data.Dataset):
+class JigSawDataset(data.Dataset):
+    def __init__(
+            self,
+            names: List[str],
+            labels: List[int],
+            path_dataset: str,
+            jig_classes=30, img_transformer: Optional[transforms.Compose] = None):
+        self.data_path = path_dataset
+        self.names = names
+        self.labels = labels
+        self.image_transformer = img_transformer
+
+        self.permutations = self.__retrieve_permutations(jig_classes)
+        self.grid_size = 3
+        self.image_resize = transforms.Compose([
+            transforms.Resize(256, Image.BILINEAR),
+            transforms.CenterCrop(255)])
+        self.augment_tile = transforms.Compose([
+            transforms.RandomCrop(64),
+            transforms.Resize((75, 75), Image.BILINEAR),
+            transforms.Lambda(rgb_jittering),
+            transforms.ToTensor()
+        ])
+
+    def get_tile(self, img, n):
+        w = float(img.size[0]) / self.grid_size
+        y = int(n / self.grid_size)
+        x = n % self.grid_size
+        tile = img.crop([x * w, y * w, (x + 1) * w, (y + 1) * w])
+        tile = self.augment_tile(tile)
+        return tile
+
+    def __getitem__(self, index):
+     # Get and process an image
+        image_path = self.data_path + "/" + self.names[index]
[…]

### 2022-01-17 data_helper.py
Update data_helper.py

@@ -1,120 +1,53 @@
 import torch
-import torch.utils.data as data
 from torchvision import transforms
-
-from dataset import Dataset, TestDataset, _dataset_info
-
-"""
-get_train_dataloader(args,txt_file) 
-Combines a dataset and a sampler, and provides an iterable over the given dataset. 
-Parameters:
-A dataset object (map style)
-args:
-path_dataset
-batch_size
-
-txt_file:
-(source_path_file/target_path_file)
+from dataset import _dataset_info, JigSawDataset, JigsawTestDataset
 
 
-"""
-# Iteration ovetr test_dataset
+
 def get_train_dataloader(args, txt_file):
-    """
-    1.train_dataset (Dataset) : dataset from which to load the data.
-    2.batch_size (int, optional) : how many samples per batch to load (default: 1).
-    3.shuffle (bool, optional) : set to True to have the data reshuffled at every epoch (default: False).
-    4.num_workers (int, optional) : how many subprocesses to use for data loading.
-    0 means that the data will be loaded in the main process. (default: 0)
-    5.pin_memory (bool, optional) : If True, the data loader will copy Tensors
-    into CUDA pinned memory before returning them.
-    If your data elements are a custom type, or your collate_fn
-    returns a batch that is a custom type, see the example below.
-
-    6.drop_last (bool, optional) : set to True to drop the last incomplete batch, if the dataset size is not divisible by the batch size. If False and the size of dataset
-    is not divisible by the batch size, then the last batch will be smaller. (default: False)
-    """
 
     img_transformer = get_train_transformers(args)
     name_train, labels_train = _dataset_info(txt_file)
-    train_dataset = Dataset(
-        name_train, labels_train, args.path_dataset, img_transformer=img_transformer
-    )
+    train_dataset = JigSawDataset(
+        name_train, labels_train, args.path_dataset, img_transformer=img_transformer)
     loader = torch.utils.data.DataLoader(
-        train_dataset,
-        batch_size=args.batch_size,
-        shuffle=True,
-        num_workers=4,
-        pin_memory=True,
-        drop_last=True,
-    )
+        train_dataset, batch_size=args.batch_size, shuffle=True, num_workers=4, pin_memory=True, drop_last=True)
 
     return loader
 
 
-# provide iteration over test_dataset
 def get_val_dataloader(args, txt_file):
 
[…]

### 2022-01-17 optimizer_helper.py
Update optimizer_helper.py

@@ -1,45 +1,17 @@
 from torch import optim
 
 
-def get_optim_and_scheduler(feature_extractor,rot_cls,obj_cls, epochs, lr, train_all):
-    """
-    Set up the optimizer and learning rate scheduler.
-
-    Parameters
-    ----------
-    feature_extractor : nn.Module
-        Feature extractor for images.
-    rot_cls : nn.Module
-        Rotation classifier.
-    obj_cls : nn.Module
-        Object classifier.
-    epochs: int
-        Number of epochs
-    lr: float
-        Learning rate
-    train_all: boolean
-        If true train all features
-
-    Returns
-    -------
-    optimizer: Optimizer
-        Optimizer algorithm
-    scheduler: torch.optim.lr_scheduler
-        Learning rate scheduler
-    """
+def get_optim_and_scheduler(feature_extractor, rot_cls, obj_cls, epochs, lr, train_all):
 
     if train_all:
-        params = list(feature_extractor.parameters()) + list(rot_cls.parameters()) + list(obj_cls.parameters())
+        params = list(feature_extractor.parameters()) + \
+            list(rot_cls.parameters()) + list(obj_cls.parameters())
     else:
         params = list(rot_cls.parameters()) + list(obj_cls.parameters())
 
-    # Using stochastic gradient descent with momentum
     optimizer = optim.SGD(params, weight_decay=.0005, momentum=.9, lr=lr)
-    
-    # Decays the learning rate of each parameter group by gamma (default 0.1) every step_size epochs
     step_size = int(epochs * .8)
     scheduler = optim.lr_scheduler.StepLR(optimizer, step_size=step_size)
-
 
     print("Step size: %d" % step_size)
     return optimizer, scheduler

### 2022-01-17 data_helper.py
Update data_helper.py

@@ -1,53 +1,120 @@
 import torch
+import torch.utils.data as data
 from torchvision import transforms
-from dataset import _dataset_info, JigSawDataset, JigsawTestDataset
+
+from dataset import Dataset, TestDataset, _dataset_info
+
+"""
+get_train_dataloader(args,txt_file) 
+Combines a dataset and a sampler, and provides an iterable over the given dataset. 
+Parameters:
+A dataset object (map style)
+args:
+path_dataset
+batch_size
+
+txt_file:
+(source_path_file/target_path_file)
 
 
-
+"""
+# Iteration ovetr test_dataset
 def get_train_dataloader(args, txt_file):
+    """
+    1.train_dataset (Dataset) : dataset from which to load the data.
+    2.batch_size (int, optional) : how many samples per batch to load (default: 1).
+    3.shuffle (bool, optional) : set to True to have the data reshuffled at every epoch (default: False).
+    4.num_workers (int, optional) : how many subprocesses to use for data loading.
+    0 means that the data will be loaded in the main process. (default: 0)
+    5.pin_memory (bool, optional) : If True, the data loader will copy Tensors
+    into CUDA pinned memory before returning them.
+    If your data elements are a custom type, or your collate_fn
+    returns a batch that is a custom type, see the example below.
+
+    6.drop_last (bool, optional) : set to True to drop the last incomplete batch, if the dataset size is not divisible by the batch size. If False and the size of dataset
+    is not divisible by the batch size, then the last batch will be smaller. (default: False)
+    """
 
     img_transformer = get_train_transformers(args)
     name_train, labels_train = _dataset_info(txt_file)
-    train_dataset = JigSawDataset(
-        name_train, labels_train, args.path_dataset, img_transformer=img_transformer)
+    train_dataset = Dataset(
+        name_train, labels_train, args.path_dataset, img_transformer=img_transformer
+    )
     loader = torch.utils.data.DataLoader(
-        train_dataset, batch_size=args.batch_size, shuffle=True, num_workers=4, pin_memory=True, drop_last=True)
+        train_dataset,
+        batch_size=args.batch_size,
+        shuffle=True,
+        num_workers=4,
+        pin_memory=True,
+        drop_last=True,
+    )
 
     return loader
 
 
+# provide iteration over test_dataset
 def get_val_dataloader(args, txt_file):
 
[…]

### 2022-01-17 optimizer_helper.py
Update optimizer_helper.py

@@ -1,17 +1,45 @@
 from torch import optim
 
 
-def get_optim_and_scheduler(feature_extractor, rot_cls, obj_cls, epochs, lr, train_all):
+def get_optim_and_scheduler(feature_extractor,rot_cls,obj_cls, epochs, lr, train_all):
+    """
+    Set up the optimizer and learning rate scheduler.
+
+    Parameters
+    ----------
+    feature_extractor : nn.Module
+        Feature extractor for images.
+    rot_cls : nn.Module
+        Rotation classifier.
+    obj_cls : nn.Module
+        Object classifier.
+    epochs: int
+        Number of epochs
+    lr: float
+        Learning rate
+    train_all: boolean
+        If true train all features
+
+    Returns
+    -------
+    optimizer: Optimizer
+        Optimizer algorithm
+    scheduler: torch.optim.lr_scheduler
+        Learning rate scheduler
+    """
 
     if train_all:
-        params = list(feature_extractor.parameters()) + \
-            list(rot_cls.parameters()) + list(obj_cls.parameters())
+        params = list(feature_extractor.parameters()) + list(rot_cls.parameters()) + list(obj_cls.parameters())
     else:
         params = list(rot_cls.parameters()) + list(obj_cls.parameters())
 
+    # Using stochastic gradient descent with momentum
     optimizer = optim.SGD(params, weight_decay=.0005, momentum=.9, lr=lr)
+    
+    # Decays the learning rate of each parameter group by gamma (default 0.1) every step_size epochs
     step_size = int(epochs * .8)
     scheduler = optim.lr_scheduler.StepLR(optimizer, step_size=step_size)
+
 
     print("Step size: %d" % step_size)
     return optimizer, scheduler

### 2022-01-17 dataset.py
permutations

@@ -85,6 +85,14 @@ class JigSawDataset(data.Dataset):
     def __len__(self):
         return len(self.names)
 
+    def __retrieve_permutations(self, classes):
+        all_perm = np.load('permutations_%d.npy' % (classes))
+        # from range [1,9] to [0,8]
+        if all_perm.min() == 1:
+            all_perm = all_perm - 1
+
+        return all_perm
+
 
 class JigsawTestDataset(data.Dataset):
     def __init__(

### 2022-01-17 data_helper.py
Updating dataset

@@ -2,7 +2,7 @@ import torch
 import torch.utils.data as data
 from torchvision import transforms
 
-from dataset import Dataset, TestDataset, _dataset_info
+from dataset import JigsawDataset, JigsawTestDataset, _dataset_info
 
 """
 get_train_dataloader(args,txt_file) 
@@ -19,6 +19,8 @@ txt_file:
 
 """
 # Iteration ovetr test_dataset
+
+
 def get_train_dataloader(args, txt_file):
     """
     1.train_dataset (Dataset) : dataset from which to load the data.
@@ -37,7 +39,7 @@ def get_train_dataloader(args, txt_file):
 
     img_transformer = get_train_transformers(args)
     name_train, labels_train = _dataset_info(txt_file)
-    train_dataset = Dataset(
+    train_dataset = JigsawDataset(
         name_train, labels_train, args.path_dataset, img_transformer=img_transformer
     )
     loader = torch.utils.data.DataLoader(
@@ -57,7 +59,8 @@ def get_val_dataloader(args, txt_file):
 
     names, labels = _dataset_info(txt_file)
     img_tr = get_test_transformer(args)
-    test_dataset = TestDataset(names, labels, args.path_dataset, img_transformer=img_tr)
+    test_dataset = JigsawTestDataset(
+        names, labels, args.path_dataset, img_transformer=img_tr)
     loader = torch.utils.data.DataLoader(
         test_dataset,
         batch_size=1,

### 2022-01-17 dataset.py

@@ -25,7 +25,7 @@ def _dataset_info(txt_labels):
     return file_names, labels
 
 
-class JigSawDataset(data.Dataset):
+class JigsawDataset(data.Dataset):
     def __init__(
             self,
             names: List[str],
@@ -45,7 +45,6 @@ class JigSawDataset(data.Dataset):
         self.augment_tile = transforms.Compose([
             transforms.RandomCrop(64),
             transforms.Resize((75, 75), Image.BILINEAR),
-            transforms.Lambda(rgb_jittering),
             transforms.ToTensor()
         ])
 
@@ -106,7 +105,6 @@ class JigsawTestDataset(data.Dataset):
         self.names = names
         self.labels = labels
         self.image_transformer = img_transformer
-
         self.permutations = self.__retrieve_permutations(jig_classes)
         self.grid_size = 3
         self.image_resize = transforms.Compose([
@@ -115,7 +113,6 @@ class JigsawTestDataset(data.Dataset):
         self.augment_tile = transforms.Compose([
             transforms.RandomCrop(64),
             transforms.Resize((75, 75), Image.BILINEAR),
-            transforms.Lambda(rgb_jittering),
             transforms.ToTensor()
         ])
 
@@ -125,7 +122,7 @@ class JigsawTestDataset(data.Dataset):
             x = n % self.grid_size
             tile = img.crop([x * w, y * w, (x + 1) * w, (y + 1) * w])
             tile = self.augment_tile(tile)
-        return tile
+            return tile
 
     def __getitem__(self, index):
         # Get and process an image
@@ -156,6 +153,14 @@ class JigsawTestDataset(data.Dataset):
 
     def __len__(self):
         return len(self.names)
+
+    def __retrieve_permutations(self, classes):
+        all_perm = np.load('permutations_%d.npy' % (classes))
+        # from range [1,9] to [0,8]
+        if all_perm.min() == 1:
+            all_perm = all_perm - 1
+
+        return all_perm
 
 
 # sphinx_gallery_thumbnail_path = "../../gallery/assets/visualization_utils_thumbnail.png"

### 2022-01-17 Report/Paper_OpenSet.tex
Report - Started method

@@
 
-ROS but without the center-loss and only a single-head rotation classifier.
+This study aims to solve the open-set scenario by using self-supervised learning with domain adaptation.
+Image rotation recognition has been chosen as the self-supervised task due to it's good performance for visual representation learning \cite{Xu2019, Gidaris2018}.
+The rotation recognition task involves taking the original image sample from the source domain and rotating it clockwise a set amount (for example by 0$^{\circ}$, 90$^{\circ}$, 180$^{\circ}$ or 270$^{\circ}$).
+A rotation classifier is then trained to predict the correct orientation of the object.
+The correct orientation of the object, however, is not an inherent property of an image, for example consider the pens in Figure \ref{fig:RotatedPens}.
+When analysing a rotated image of a pen it is not possible to infer the original rotation.
+The original image is therefore included in the rotation classifier and the relative rotation analysed instead.
+In training the rotation classifier the features of the original sample are concatenated with the features of the rotated sample.
+By including the original samples the network is also able to learn features that are more discriminative between class labels, focussing more on the shape of the object and less on the texture \cite{Bucci2020}, as shown in Figure \ref{fig:RotationFeatures}.
+
+\begin{figure}[!htb]
+  \centering
+   \includegraphics[width=0.9\linewidth]{Figures/RotatedPens.png}
+   \caption{Relative orientations of pens with respect to the original images \cite{Bucci2020}.}
+   \label{fig:RotatedPens}
+\end{figure}
+
+\begin{figure}[!htb]
+  \centering
+   \includegraphics[width=0.9\linewidth]{Figures/RotationFeatures.png}
+   \caption{Image rotations help the network learn features that discriminate the shape of objects \cite{Bucci2020}.}
+   \label{fig:RotationFeatures}
+\end{figure}
+
+To solve the open-set domain adaptation problem a simplified version of the ROS method (Figure \ref{fig:ROS}) is used.
+This version uses a single-head rotation classifier and does not include the center-loss, \textcolor{red}{however the effect of the center-loss is evaluated subsequently as a variation to this method}.
+Alternative self-supervised tasks are also considered, including horizontal flipping, \textcolor{red}{vertical flipping} and through solving jigsaw puzzles.
+These variations are analyzed in Section \ref{sec:variations}.
+
+\begin{figure*}[!htb]
+  \centering
+   \includegraphics[width=0.9\linewidth]{Figures/ROS.png}
+   \caption{Rotation-based Open Set (ROS) method schematic illustration \cite{Bucci2020}.}
+   \label{fig:ROS}
+\end{figure*}
+
+\subsection{Stage I - known/unknown separation}
+
+Stage I of the simplified ROS method involves training both an object classifier and a rotation recognition task on data from the source domain, as shown on the left side of Figure \ref{fig:ROS}.
+
+\subsection{Target evaluation}
+
+\subsection{Stage II - domain alignment}
+
+\subsection{Final evaluation}
 
 - describe in detail the method used
-- the network used
 - include the diagrams here and explain them
@@
 
+- the network used
 - ablation study: hyperparameter tuning of weights and threshold value, include graphs or tables of values

### 2022-01-17 Report/Paper_OpenSet.tex
Report - Method - Step 1

@@
 
-Stage I of the simplified ROS method involves training both an object classifier and a rotation recognition task on data from the source domain, as shown on the left side of Figure \ref{fig:ROS}.
+Stage I of the simplified ROS method involves training both an object classifier and a rotation recognition task on data from the source domain, as shown on the left side of Figure \ref{fig:ROS}, where $D_S$ is the source domain dataset, $E$ is the encoder, $C_1$ is the object classifier and $R_1$ is the rotation classifier.
+The object prediction is based on the features of the original source samples, whereas the rotation prediction is based on the concatenated features of the original and rotated samples.
+The object classification and rotation recognition tasks are trained simultaneously to minimize the total loss objective function given by:
+\begin{equation}
+  L_{tot} = L_{cls} + \alpha_1 L_{rot} ,
+  \label{eq:totalloss}
+\end{equation}
+where $L_{cls}$ is the loss from the object classifier, $L_{rot}$ is the loss from the rotation classifier, and $\alpha_1$ is the weight assigned to the rotation recognition task.
+The value of $\alpha_1$ is tuned according to the performance of the network, as detailed in Section \ref{sec:ablation}.
 
@@
 \label{sec:experiments}
+
+\subsection{Ablation study}
+\label{sec:ablation}
+
+\subsection{Results}
 

### 2022-01-17 Report/Paper_OpenSet.tex
Report - Method - Target evaluation

@@
 
-Stage I of the simplified ROS method involves training both an object classifier and a rotation recognition task on data from the source domain, as shown on the left side of Figure \ref{fig:ROS}, where $D_S$ is the source domain dataset, $E$ is the encoder, $C_1$ is the object classifier and $R_1$ is the rotation classifier.
+Stage I of the simplified ROS method involves training both an object classifier and a rotation recognition task on data from the source domain, as shown on the left side of Figure \ref{fig:ROS}, where $D_s$ is the source domain dataset, $E$ is the encoder, $C_1$ is the object classifier and $R_1$ is the rotation classifier.
 The object prediction is based on the features of the original source samples, whereas the rotation prediction is based on the concatenated features of the original and rotated samples.
@@
 
-\subsection{Target evaluation}
+\subsubsection*{Target evaluation}
+
+Once the rotation classifier has been well trained it can be used to identify the known classes of the target domain, and separate these samples from the unknown classes.
+The method is illustrated in the center of Figure \ref{fig:ROS}, where $D_t$ is the target domain dataset, $D_t^{unk}$ is the dataset of target samples identified as belonging to an unknown class, and $D^{knw}_t$ is the dataset of target samples identified as belonging to a known class.
+The rotation classifier is applied to each of the target samples and generates a score for each of the possible rotations.
+The normality score is then computed as the rotation with the maximum score (highest prediction).
+
+The precision of the normality score is then evaluated using the AUROC (Area Under Receiver Operating Characteristics curve) metric.
+The AUROC metric reduces analysis of the ROC curve to a single scalar value which can be used to compare the performance of classifiers \cite{Fawcett2006}.
+The higher the AUROC score the better the classifier overall, with scores $> 0.5$ showing an improvement over random guessing.
+
+If the AUROC is $> 0.5$ then the normality score can be used to conduct the known/unknown separation subject to a selected threshold, i.e.
+if the normality score is above the threshold the sample is considered as known and added to $D^{knw}_t$, otherwise it is considered as unknown and added to $D_t^{unk}$.
+The threshold value is also tuned according to the performance of the network, as detailed in Section \ref{sec:ablation}.
 
@@
 
-\subsection{Final evaluation}
+\subsubsection*{Final evaluation}
 

### 2022-01-17 center_loss.py
updating centerLoss

@@ -16,19 +16,21 @@ class CenterLoss(nn.Module):
     ----------
     Wen et al. A Discriminative Feature Learning Approach for Deep Face Recognition. ECCV 2016.
     """
-
+    
     def __init__(self, num_classes: int = 10, feat_dim: int = 2, use_gpu: bool = True):
         super(CenterLoss, self).__init__()
         self.num_classes = num_classes
         self.feat_dim = feat_dim
         self.use_gpu = use_gpu
+        print(self.use_gpu)
 
         if self.use_gpu:
             self.centers = nn.Parameter(
                 torch.randn(self.num_classes, self.feat_dim).cuda()
             )
         else:
-            self.centers = nn.Parameter(torch.randn(self.num_classes, self.feat_dim))
+            self.centers = nn.Parameter(
+                torch.randn(self.num_classes, self.feat_dim))
 
     def forward(self, x: torch.Tensor, labels: torch.Tensor):
         """
@@ -39,6 +41,7 @@ class CenterLoss(nn.Module):
         labels: Tensor
             ground truth labels with shape (batch_size).
         """
+       
         batch_size = x.size(0)
         distmat = (
             torch.pow(x, 2)

### 2022-01-17 main.py

@@ -9,6 +9,8 @@ from step1_KnownUnknownSep import step1
 from eval_target import evaluation
 from step2_SourceTargetAdapt import step2
 
+from center_loss import CenterLoss
+
 
 def get_args():
     """
@@ -57,7 +59,8 @@ def get_args():
     parser.add_argument(
         "--max_scale", default=1.0, type=float, help="Maximum scale percent"
     )
-    parser.add_argument("--jitter", default=0.4, type=float, help="Color jitter amount")
+    parser.add_argument("--jitter", default=0.4, type=float,
+                        help="Color jitter amount")
     parser.add_argument(
         "--random_grayscale",
         default=0.1,
@@ -66,8 +69,10 @@ def get_args():
     )
 
     # training parameters
-    parser.add_argument("--image_size", type=int, default=222, help="Image size")
-    parser.add_argument("--batch_size", type=int, default=128, help="Batch size")
+    parser.add_argument("--image_size", type=int,
+                        default=222, help="Image size")
+    parser.add_argument("--batch_size", type=int,
+                        default=128, help="Batch size")
     parser.add_argument(
         "--learning_rate", type=float, default=0.001, help="Learning rate"
     )
@@ -113,6 +118,19 @@ def get_args():
         help="Threshold for the known/unkown separation",
     )
 
+    # centerLoss params
+    parser.add_argument('--lr_cent', type=float, default=0.5,
+                        help="learning rate for center loss")
+    parser.add_argument('--weight_cent', type=float,
+                        default=1, help="weight for center loss")
+    parser.add_argument('--max_epoch', type=int, default=100)
+    parser.add_argument('--stepsize', type=int, default=20)
+    parser.add_argument('--gamma', type=float, default=0.5,
+                        help="learning rate decay")
+
+    parser.add_argument('--plot', action='store_true',
+                        help="whether to plot features for every epoch")
+
     # tensorboard logger
     parser.add_argument(
         "--tf_logger",
@@ -152,7 +170,8 @@ class Trainer:
         self.args = args
 
         # Set device for allocation of the tensor
-        self.device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+        self.device = torch.device(
+            "cuda" if torch.cuda.is_available() else "cpu")
 
         # ResNet model
         self.feature_extractor = resnet18_feat_extractor()
@@ -160,6 +179,12 @@ class Trainer:
         self.obj_classifier = Classifier(512, self.args.n_classes_known + 1)
[…]

### 2022-01-17 optimizer_helper.py

@@ -1,7 +1,7 @@
 from torch import optim
 
 
-def get_optim_and_scheduler(feature_extractor,rot_cls,obj_cls, epochs, lr, train_all):
+def get_optim_and_scheduler(feature_extractor, rot_cls, obj_cls, center_loss, epochs, lr, train_all):
     """
     Set up the optimizer and learning rate scheduler.
 
@@ -29,17 +29,18 @@ def get_optim_and_scheduler(feature_extractor,rot_cls,obj_cls, epochs, lr, train
     """
 
     if train_all:
-        params = list(feature_extractor.parameters()) + list(rot_cls.parameters()) + list(obj_cls.parameters())
+        params = list(feature_extractor.parameters()) + list(rot_cls.parameters()
+                                                             ) + list(obj_cls.parameters()) + list(center_loss.parameters())
     else:
-        params = list(rot_cls.parameters()) + list(obj_cls.parameters())
+        params = list(rot_cls.parameters()) + \
+            list(obj_cls.parameters()) + list(center_loss.parameters())
 
     # Using stochastic gradient descent with momentum
     optimizer = optim.SGD(params, weight_decay=.0005, momentum=.9, lr=lr)
-    
+
     # Decays the learning rate of each parameter group by gamma (default 0.1) every step_size epochs
     step_size = int(epochs * .8)
     scheduler = optim.lr_scheduler.StepLR(optimizer, step_size=step_size)
-
 
     print("Step size: %d" % step_size)
     return optimizer, scheduler

### 2022-01-17 step1_KnownUnknownSep.py

@@ -7,8 +7,13 @@ from torch import nn
 from torch.utils.data import DataLoader
 from resnet import ResNet, Classifier
 import os
+import matplotlib
+from matplotlib import pyplot as plt
+from center_loss import CenterLoss
+import numpy as np
 
-#### Implement Step1
+
+# Implement Step1
 
 
 def _do_epoch(
@@ -16,6 +21,7 @@ def _do_epoch(
     feature_extractor: ResNet,
     rot_cls: Classifier,
     obj_cls: Classifier,
+    center_loss: CenterLoss,
     source_loader: DataLoader,
     optimizer: torch.optim.Optimizer,
     device: torch.device,
@@ -52,6 +58,10 @@ def _do_epoch(
         Accuracy for rotation recognition
     """
     criterion = nn.CrossEntropyLoss()
+    # Initialize center loss
+    
+    center_loss = CenterLoss(args.n_classes_known*4,
+                             256*args.n_classes_known, False)
     feature_extractor.train()
     obj_cls.train()
     rot_cls.train()
@@ -73,16 +83,25 @@ def _do_epoch(
         # Pass features to classifiers
         class_scores = obj_cls(original_features)
         # Here we have to concatenate tensors as suggested by the architecture
-        rotation_scores = rot_cls(torch.cat([original_features, rotated_features], 1))
+        rotation_scores = rot_cls(
+            torch.cat([original_features, rotated_features], 1))
+
+        # Concatenation of the features
+        features = torch.cat([original_features, rotated_features], 1)
 
         # Now we can check the losses
         class_loss = criterion(class_scores, class_label)
-        # TODO: This needs CenterLoss to work better (see variation 3)
-        rot_loss = criterion(rotation_scores, rotated_label)
+        #  This needs CenterLoss to work better (see variation 3)
+        cent_loss = center_loss(features, rotated_label) * args.weight_cent
+        rot_loss = criterion(rotation_scores, rotated_label) + cent_loss
 
         loss = class_loss + args.weight_RotTask_step1 * rot_loss
 
         loss.backward()
+        for param in center_loss.parameters():
+            # lr_cent is learning rate for center loss, e.g. lr_cent = 0.5
+            param.grad.data *= (args.lr_cent /
+                                (args.weight_cent * args.learning_rate))
 
         optimizer.step()
 
@@ -92,7 +111,8 @@ def _do_epoch(
 
[…]

### 2022-01-18 Report/Paper_OpenSet.tex
Report - completed method

@@
 
+In stage II of the simplified ROS method the unknown dataset created from the target domain $D_t^{unk}$ is combined with the samples from the source domain $D_s$, with the unknown samples representing an additional `unknown' class.
+The object classifier $C_2$ is thus trained to recognise samples belonging to the unknown class.
+Concurrently, the known target samples  $D^{knw}_t$ are used for the source-target adaptation by training the rotation recognition task $R_2$.
+The method is shown on the right side of Figure \ref{fig:ROS}.
+As in stage I, the object classification and rotation recognition tasks are trained simultaneously to minimize the total loss objective function given by:
+\begin{equation}
+  L_{tot} = L_{cls} + \alpha_2 L_{rot} ,
+  \label{eq:totalloss}
+\end{equation}
+where $\alpha_2$ is the weight assigned to the rotation recognition task of stage II.
+The value of $\alpha_2$ is also selected to provide the best performance, detailed further in Section \ref{sec:ablation}.
+
 \subsubsection*{Final evaluation}
 
-- describe in detail the method used
-- include the diagrams here and explain them
-- explain the evaluation parameters that will be used
+Once the classifiers have been trained the final evaluation can be completed.
+Three metrics are considered for the evalutation: the accuracy of the object classifier in correctly classifying objects of the known category $OS^*$; the accuracy of the object classifier in correctly identifying objects of the unknown category $UNK$; and the harmonic mean $HOS$ between the two accuracys $OS^*$ and $UNK$, as defined in \cite{Bucci2020}.
+The harmonic mean is calculated as:
+\begin{equation}
+ HOS = 2\, \frac{OS^* \times UNK}{OS^* + UNK} ,
+ \label{eq:hos}
+\end{equation}
+and provides a balanced measure of performance of the classifier at recognizing both known and unknown samples.
 
@@
 
+- the network used
+
 \subsection{Ablation study}
@@
 
+- ablation study: hyperparameter tuning of weights and threshold value, include graphs or tables of values
+
 \subsection{Results}
-
-- the network used
-- ablation study: hyperparameter tuning of weights and threshold value, include graphs or tables of values
 

### 2022-01-19 data_helper.py
new implementation of jig

@@ -42,6 +42,7 @@ def get_train_dataloader(args, txt_file):
     train_dataset = JigsawDataset(
         name_train, labels_train, args.path_dataset, img_transformer=img_transformer
     )
+
     loader = torch.utils.data.DataLoader(
         train_dataset,
         batch_size=args.batch_size,
@@ -59,6 +60,7 @@ def get_val_dataloader(args, txt_file):
 
     names, labels = _dataset_info(txt_file)
     img_tr = get_test_transformer(args)
+
     test_dataset = JigsawTestDataset(
         names, labels, args.path_dataset, img_transformer=img_tr)
     loader = torch.utils.data.DataLoader(

### 2022-01-19 dataset.py

@@ -1,14 +1,16 @@
-import torch.utils.data as data
-from PIL import Image
-from random import random
-import random
-import torchvision
-import torchvision.transforms.functional as TF
-import torch
 import numpy as np
+import torch
+import torch.utils.data as data
+import torchvision
+import torchvision.transforms as transforms
+from PIL import Image
+import random
+from random import sample, random
+import torchvision.transforms.functional as TF
 import matplotlib.pyplot as plt
 from typing import List, Optional
-import torchvision.transforms as transforms
+import torchvision.transforms.functional as F
+import os
 
 
 def _dataset_info(txt_labels):
@@ -35,7 +37,9 @@ class JigsawDataset(data.Dataset):
         self.data_path = path_dataset
         self.names = names
         self.labels = labels
-        self.image_transformer = img_transformer
+        self.image_transformer = transforms.Compose([
+            transforms.Resize(256, Image.BILINEAR),
+            transforms.CenterCrop(255)])
 
         self.permutations = self.__retrieve_permutations(jig_classes)
         self.grid_size = 3
@@ -60,26 +64,74 @@ class JigsawDataset(data.Dataset):
      # Get and process an image
         image_path = self.data_path + "/" + self.names[index]
         img = Image.open(image_path).convert("RGB")
-        if self.image_transformer:
-            img = self.image_transformer(img)
+        # if self.image_transformer:
+        #  img = self.image_transformer(img)
 
-        if img.size[0] != 255:
-            img = self.image_resize(img)
+       # if img.size[0] != 255:
+        #  img = self.image_resize(img)
 
         # 9 is number of grids
+        """
         tiles = [None] * 9
-        for n in range(n_grids):
+        for n in range(9):
             tiles[n] = self.get_tile(img, n)
 
-        index = random.randrange(len(self.permutations) + 1)
+        index = np.random.randint(len(self.permutations) + 1)
         if index == 0:
             data = tiles
         else:
-            data = [tiles[self.permutations[order - 1][t]]
-                    for t in range(n_grids)]
+            data = [tiles[self.permutations[index - 1][t]]
+                    for t in range(9)]
 
         data = torch.stack(data, 0)
-        return img, int(self.labels[index]), data, int(index)
[…]

### 2022-01-19 step1_KnownUnknownSep.py

@@ -8,7 +8,7 @@ from torch.utils.data import DataLoader
 from resnet import ResNet, Classifier
 import os
 
-#### Implement Step1
+# Implement Step1
 
 
 def _do_epoch(
@@ -73,7 +73,8 @@ def _do_epoch(
         # Pass features to classifiers
         class_scores = obj_cls(original_features)
         # Here we have to concatenate tensors as suggested by the architecture
-        rotation_scores = rot_cls(torch.cat([original_features, rotated_features], 1))
+        rotation_scores = rot_cls(
+            torch.cat([original_features, rotated_features], 1))
 
         # Now we can check the losses
         class_loss = criterion(class_scores, class_label)
@@ -92,7 +93,8 @@ def _do_epoch(
 
         # Update counters
         correct_classes += torch.sum(class_prediction == class_label).item()
-        correct_rotations += torch.sum(rotation_prediction == rotated_label).item()
+        correct_rotations += torch.sum(rotation_prediction ==
+                                       rotated_label).item()
 
     acc_cls = correct_classes / len(source_loader.dataset)
     acc_rot = correct_rotations / len(source_loader.dataset)
@@ -130,8 +132,11 @@ def step1(
             if not os.path.isdir("weights"):
                 os.mkdir("weights")
             torch.save(
-                feature_extractor.state_dict(), f"weights/feature_extractor_{epoch}.pth"
+                feature_extractor.state_dict(
+                ), f"weights/feature_extractor_{epoch}.pth"
             )
-            torch.save(obj_cls.state_dict(), f"weights/object_classifier_{epoch}.pth")
-            torch.save(rot_cls.state_dict(), f"weights/rotation_classifier_{epoch}.pth")
+            torch.save(obj_cls.state_dict(),
+                       f"weights/object_classifier_{epoch}.pth")
+            torch.save(rot_cls.state_dict(),
+                       f"weights/rotation_classifier_{epoch}.pth")
         scheduler.step()

### 2022-01-19 dataset.py
solving some bugs

@@ -64,9 +64,10 @@ class JigsawDataset(data.Dataset):
      # Get and process an image
         image_path = self.data_path + "/" + self.names[index]
         img = Image.open(image_path).convert("RGB")
-        # if self.image_transformer:
-        #  img = self.image_transformer(img)
-
+        if self.image_transformer:
+          img = self.image_transformer(img)
+        
+        
        # if img.size[0] != 255:
         #  img = self.image_resize(img)
 
@@ -87,8 +88,8 @@ class JigsawDataset(data.Dataset):
         img = transforms.ToTensor()(img)
         """
 
-      #  if np.random.rand() < 0.30:
-       #     img = img.convert('LA').convert('RGB')
+        if np.random.rand() < 0.30:
+            img = img.convert('LA').convert('RGB')
 
         if img.size[0] != 255:
             img = self.image_transformer(img)
@@ -114,20 +115,15 @@ class JigsawDataset(data.Dataset):
 
         order = np.random.randint(len(self.permutations))
         data = [tiles[self.permutations[order][t]] for t in range(9)]
-        lst = []
-        x=0
-        for i in range(9):
-             lst.append(data[i])
-        # lstt = torch.stack([x for _ in range(10)])
-        #lstt = torch.stack(lst)
-
-        data = torch.cat(data, 1)
-
-
-
+        data1 = torch.cat(data[0:3], 2)
+        data2 = torch.cat(data[3:6], 2)
+        data3 = torch.cat(data[6:9], 2)
+        data = torch.cat((data1, data2, data3), 1)
+        
+        
         img = transforms.ToTensor()(img)
-    
-        #data = torch.squeeze(data)
+        
+        
 
         #show([img, data])
 

### 2022-01-19 main.py

@@ -159,7 +159,7 @@ class Trainer:
         # Initiate object classifier with input_size=512, and numbers of classes is known classes + 1 (the unknown class, trained only in step2)
         self.obj_classifier = Classifier(512, self.args.n_classes_known + 1)
         # Initiate rotation classifier with input_size=512*2 and 4 classes: [0, 90, 180, 270]
-        self.rot_classifier = Classifier(512 * 2, 4)
+        self.rot_classifier = Classifier(512 * 4, 30)
 
         if args.load_weights:
             self.rot_classifier.load_state_dict(

### 2022-01-19 resnet.py

@@ -14,7 +14,8 @@ class ResNet(nn.Module):
         self.inplanes = 64
         super(ResNet, self).__init__()
         # Layers
-        self.conv1 = nn.Conv2d(3, 64, kernel_size=7, stride=2, padding=3, bias=False)
+        self.conv1 = nn.Conv2d(3, 64, kernel_size=7,
+                               stride=2, padding=3, bias=False)
         self.bn1 = nn.BatchNorm2d(64)
         self.relu = nn.ReLU(inplace=True)
         self.maxpool = nn.MaxPool2d(kernel_size=3, stride=2, padding=1)
@@ -30,7 +31,8 @@ class ResNet(nn.Module):
         # Init layers
         for m in self.modules():
             if isinstance(m, nn.Conv2d):
-                nn.init.kaiming_normal_(m.weight, mode="fan_out", nonlinearity="relu")
+                nn.init.kaiming_normal_(
+                    m.weight, mode="fan_out", nonlinearity="relu")
             elif isinstance(m, nn.BatchNorm2d):
                 nn.init.constant_(m.weight, 1)
                 nn.init.constant_(m.bias, 0)
@@ -100,6 +102,7 @@ def resnet18_feat_extractor() -> ResNet:
     See here to have a better idea of the architecture: https://learnopencv.com/wp-content/uploads/2020/03/resnet-18.png
     """
     model = ResNet(BasicBlock, [2, 2, 2, 2])
-    model.load_state_dict(model_zoo.load_url(model_urls["resnet18"]), strict=False)
+    model.load_state_dict(model_zoo.load_url(
+        model_urls["resnet18"]), strict=False)
 
     return model

### 2022-01-19 eval_target.py
updating parameters

@@ -66,9 +66,9 @@ def evaluation(
             )
             original_features = feature_extractor(data)
 
-            entropy_losses = torch.zeros([4])
-            rotation_scores = torch.zeros([4])
-            for i in range(4):
+            entropy_losses = torch.zeros([30])
+            rotation_scores = torch.zeros([30])
+            for i in range(30):
                 rotated = torch.rot90(data, k=i, dims=[2, 3])
                 rotated_features = feature_extractor(rotated)
                 rotation_probabilities = torch.nn.Softmax(dim=0)(

### 2022-01-19 dataset.py
fixing

@@ -38,14 +38,14 @@ class JigsawDataset(data.Dataset):
         self.names = names
         self.labels = labels
         self.image_transformer = transforms.Compose([
-            transforms.Resize(256, Image.BILINEAR),
-            transforms.CenterCrop(255)])
+            transforms.Resize(224, Image.BILINEAR),
+            transforms.CenterCrop(224)])
 
         self.permutations = self.__retrieve_permutations(jig_classes)
         self.grid_size = 3
         self.image_resize = transforms.Compose([
-            transforms.Resize(256, Image.BILINEAR),
-            transforms.CenterCrop(255)])
+            transforms.Resize(224, Image.BILINEAR),
+            transforms.CenterCrop(224)])
         self.augment_tile = transforms.Compose([
             transforms.RandomCrop(64),
             transforms.Resize((75, 75), Image.BILINEAR),
@@ -88,8 +88,7 @@ class JigsawDataset(data.Dataset):
         img = transforms.ToTensor()(img)
         """
 
-        if np.random.rand() < 0.30:
-            img = img.convert('LA').convert('RGB')
+       
 
         if img.size[0] != 255:
             img = self.image_transformer(img)
@@ -123,9 +122,10 @@ class JigsawDataset(data.Dataset):
         
         img = transforms.ToTensor()(img)
         
-        
+        print(data.shape)
+        print(img.shape)
 
-        #show([img, data])
+        show([img, data])
 
         return img, int(self.labels[index]), data, int(order)
 

### 2022-01-19 main.py

@@ -57,7 +57,8 @@ def get_args():
     parser.add_argument(
         "--max_scale", default=1.0, type=float, help="Maximum scale percent"
     )
-    parser.add_argument("--jitter", default=0.4, type=float, help="Color jitter amount")
+    parser.add_argument("--jitter", default=0.4, type=float,
+                        help="Color jitter amount")
     parser.add_argument(
         "--random_grayscale",
         default=0.1,
@@ -66,8 +67,10 @@ def get_args():
     )
 
     # training parameters
-    parser.add_argument("--image_size", type=int, default=222, help="Image size")
-    parser.add_argument("--batch_size", type=int, default=128, help="Batch size")
+    parser.add_argument("--image_size", type=int,
+                        default=222, help="Image size")
+    parser.add_argument("--batch_size", type=int,
+                        default=128, help="Batch size")
     parser.add_argument(
         "--learning_rate", type=float, default=0.001, help="Learning rate"
     )
@@ -152,14 +155,15 @@ class Trainer:
         self.args = args
 
         # Set device for allocation of the tensor
-        self.device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+        self.device = torch.device(
+            "cuda" if torch.cuda.is_available() else "cpu")
 
         # ResNet model
         self.feature_extractor = resnet18_feat_extractor()
         # Initiate object classifier with input_size=512, and numbers of classes is known classes + 1 (the unknown class, trained only in step2)
-        self.obj_classifier = Classifier(512, self.args.n_classes_known + 1)
+        self.obj_classifier = Classifier(512*2, self.args.n_classes_known + 1)
         # Initiate rotation classifier with input_size=512*2 and 4 classes: [0, 90, 180, 270]
-        self.rot_classifier = Classifier(512 * 4, 30)
+        self.rot_classifier = Classifier(512*2, 30)
 
         if args.load_weights:
             self.rot_classifier.load_state_dict(
@@ -183,7 +187,8 @@ class Trainer:
         # Path to file with the list of known class images, source is the domain of the image (from command line argument, default is Art)
         source_path_file = "txt_list/" + args.source + "_known.txt"
         # Create the source data loader, providing an iterable over the dataset - using map-style dataset.
-        self.source_loader = data_helper.get_train_dataloader(args, source_path_file)
+        self.source_loader = data_helper.get_train_dataloader(
+            args, source_path_file)
 
[…]

### 2022-01-19 dataset.py
JigsawPuzzle now work (Probably)

@@ -1,3 +1,4 @@
+import enum
 import numpy as np
 import torch
 import torch.utils.data as data
@@ -11,16 +12,17 @@ import matplotlib.pyplot as plt
 from typing import List, Optional
 import torchvision.transforms.functional as F
 import os
+from itertools import product
 
 
 def _dataset_info(txt_labels):
-    with open(txt_labels, 'r') as f:
+    with open(txt_labels, "r") as f:
         images_list = f.readlines()
 
     file_names = []
     labels = []
     for row in images_list:
-        row = row.split(' ')
+        row = row.split(" ")
         file_names.append(row[0])
         labels.append(int(row[1]))
 
@@ -29,89 +31,29 @@ def _dataset_info(txt_labels):
 
 class JigsawDataset(data.Dataset):
     def __init__(
-            self,
-            names: List[str],
-            labels: List[int],
-            path_dataset: str,
-            jig_classes=30, img_transformer: Optional[transforms.Compose] = None):
+        self,
+        names: List[str],
+        labels: List[int],
+        path_dataset: str,
+        jig_classes=30,
+        img_transformer: Optional[transforms.Compose] = None,
+    ):
         self.data_path = path_dataset
         self.names = names
         self.labels = labels
-        self.image_transformer = transforms.Compose([
-            transforms.Resize(256, Image.BILINEAR),
-            transforms.CenterCrop(255)])
+        self.image_transformer = transforms.Resize(216)
 
         self.permutations = self.__retrieve_permutations(jig_classes)
-        self.grid_size = 3
-        self.image_resize = transforms.Compose([
-            transforms.Resize(256, Image.BILINEAR),
-            transforms.CenterCrop(255)])
-        self.augment_tile = transforms.Compose([
-            transforms.RandomCrop(64),
-            transforms.Resize((75, 75), Image.BILINEAR),
-            transforms.ToTensor()
-        ])
-
-    def get_tile(self, img, n):
-        w = float(img.size[0]) / self.grid_size
-        y = int(n / self.grid_size)
-        x = n % self.grid_size
-        tile = img.crop([x * w, y * w, (x + 1) * w, (y + 1) * w])
-        tile = self.augment_tile(tile)
-        return tile
 
     def __getitem__(self, index):
-     # Get and process an image
+        # Get and process an image
         image_path = self.data_path + "/" + self.names[index]
[…]

### 2022-01-19 main.py

@@ -159,7 +159,7 @@ class Trainer:
         # Initiate object classifier with input_size=512, and numbers of classes is known classes + 1 (the unknown class, trained only in step2)
         self.obj_classifier = Classifier(512, self.args.n_classes_known + 1)
         # Initiate rotation classifier with input_size=512*2 and 4 classes: [0, 90, 180, 270]
-        self.rot_classifier = Classifier(512 * 4, 30)
+        self.rot_classifier = Classifier(512 * 2, 30)
 
         if args.load_weights:
             self.rot_classifier.load_state_dict(

### 2022-01-20 step2_SourceTargetAdapt.py
Added weight saving to step 2

@@ -3,7 +3,7 @@ from torch import nn
 from optimizer_helper import get_optim_and_scheduler
 from itertools import cycle
 import numpy as np
-
+import os
 
 #### Implement Step2
 
@@ -228,4 +228,12 @@ def step2(
             optimizer,
             device,
         )
+        if epoch % 10 == 0:
+            if not os.path.isdir("weights"):
+                os.mkdir("weights")
+            torch.save(
+                feature_extractor.state_dict(), f"weights/step2_feature_extractor_{epoch}.pth"
+            )
+            torch.save(obj_cls.state_dict(), f"weights/step2_object_classifier_{epoch}.pth")
+            torch.save(rot_cls.state_dict(), f"weights/step2_rotation_classifier_{epoch}.pth")
         scheduler.step()

### 2022-01-20 dataset.py
Update jigsawTestDataset

@@ -90,50 +90,28 @@ class JigsawTestDataset(data.Dataset):
         self.data_path = path_dataset
         self.names = names
         self.labels = labels
-        self.image_transformer = img_transformer
-        self.permutations = self.__retrieve_permutations(jig_classes)
-        self.grid_size = 3
-        self.image_resize = transforms.Compose(
-            [transforms.Resize(256, Image.BILINEAR), transforms.CenterCrop(255)]
-        )
-        self.augment_tile = transforms.Compose(
-            [
-                transforms.RandomCrop(64),
-                transforms.Resize((75, 75), Image.BILINEAR),
-                transforms.ToTensor(),
-            ]
-        )
+        self.image_transformer = transforms.Resize(216)
 
-        def get_tile(self, img, n):
-            w = float(img.size[0]) / self.grid_size
-            y = int(n / self.grid_size)
-            x = n % self.grid_size
-            tile = img.crop([x * w, y * w, (x + 1) * w, (y + 1) * w])
-            tile = self.augment_tile(tile)
-            return tile
+        self.permutations = self.__retrieve_permutations(jig_classes)
 
     def __getitem__(self, index):
-        # Get and process an image
+          # Get and process an image
         image_path = self.data_path + "/" + self.names[index]
-        img = Image.open(image_path).convert("RGB")
-        if self.image_transformer:
-            img = self.image_transformer(img)
+        img = TF.resize(Image.open(image_path).convert("RGB"), [222, 222])
 
-        if img.size[0] != 255:
-            img = self.image_resize(img)
+        tiles = [
+            TF.to_tensor(TF.crop(img, 74 * row, 74 * column, 74, 74))
+            for row, column in product(range(3), range(3))
+        ]
 
-        # 9 is number of grids
-        tiles = [None] * 9
-        for n in range(n_grids):
-            tiles[n] = self.get_tile(img, n)
+        order = np.random.randint(len(self.permutations))
+        data = [tiles[self.permutations[order][t]] for t in range(9)]
+        data1 = torch.cat(data[0:3], 2)
+        data2 = torch.cat(data[3:6], 2)
+        data3 = torch.cat(data[6:9], 2)
+        data = torch.cat((data1, data2, data3), 1)
 
-        index = random.randrange(len(self.permutations) + 1)
-        if index == 0:
-            data = tiles
-        else:
-            data = [tiles[self.permutations[index - 1][t]] for t in range(n_grids)]
-
[…]

### 2022-01-20 center_loss.py
CenterLoss working (Probably)

@@ -16,7 +16,7 @@ class CenterLoss(nn.Module):
     ----------
     Wen et al. A Discriminative Feature Learning Approach for Deep Face Recognition. ECCV 2016.
     """
-    
+
     def __init__(self, num_classes: int = 10, feat_dim: int = 2, use_gpu: bool = True):
         super(CenterLoss, self).__init__()
         self.num_classes = num_classes
@@ -29,8 +29,7 @@ class CenterLoss(nn.Module):
                 torch.randn(self.num_classes, self.feat_dim).cuda()
             )
         else:
-            self.centers = nn.Parameter(
-                torch.randn(self.num_classes, self.feat_dim))
+            self.centers = nn.Parameter(torch.randn(self.num_classes, self.feat_dim))
 
     def forward(self, x: torch.Tensor, labels: torch.Tensor):
         """
@@ -41,7 +40,7 @@ class CenterLoss(nn.Module):
         labels: Tensor
             ground truth labels with shape (batch_size).
         """
-       
+
         batch_size = x.size(0)
         distmat = (
             torch.pow(x, 2)
@@ -52,7 +51,7 @@ class CenterLoss(nn.Module):
             .expand(self.num_classes, batch_size)
             .t()
         )
-        distmat.addmm_(1, -2, x, self.centers.t())
+        distmat.addmm_(x, self.centers.t(), beta=1, alpha=-2)
 
         classes = torch.arange(self.num_classes).long()
         if self.use_gpu:

### 2022-01-20 main.py

@@ -59,8 +59,7 @@ def get_args():
     parser.add_argument(
         "--max_scale", default=1.0, type=float, help="Maximum scale percent"
     )
-    parser.add_argument("--jitter", default=0.4, type=float,
-                        help="Color jitter amount")
+    parser.add_argument("--jitter", default=0.4, type=float, help="Color jitter amount")
     parser.add_argument(
         "--random_grayscale",
         default=0.1,
@@ -69,10 +68,8 @@ def get_args():
     )
 
     # training parameters
-    parser.add_argument("--image_size", type=int,
-                        default=222, help="Image size")
-    parser.add_argument("--batch_size", type=int,
-                        default=128, help="Batch size")
+    parser.add_argument("--image_size", type=int, default=222, help="Image size")
+    parser.add_argument("--batch_size", type=int, default=128, help="Batch size")
     parser.add_argument(
         "--learning_rate", type=float, default=0.001, help="Learning rate"
     )
@@ -119,17 +116,19 @@ def get_args():
     )
 
     # centerLoss params
-    parser.add_argument('--lr_cent', type=float, default=0.5,
-                        help="learning rate for center loss")
-    parser.add_argument('--weight_cent', type=float,
-                        default=1, help="weight for center loss")
-    parser.add_argument('--max_epoch', type=int, default=100)
-    parser.add_argument('--stepsize', type=int, default=20)
-    parser.add_argument('--gamma', type=float, default=0.5,
-                        help="learning rate decay")
+    parser.add_argument(
+        "--lr_cent", type=float, default=0.5, help="learning rate for center loss"
+    )
+    parser.add_argument(
+        "--weight_cent", type=float, default=1, help="weight for center loss"
+    )
+    parser.add_argument("--max_epoch", type=int, default=100)
+    parser.add_argument("--stepsize", type=int, default=20)
+    parser.add_argument("--gamma", type=float, default=0.5, help="learning rate decay")
 
-    parser.add_argument('--plot', action='store_true',
-                        help="whether to plot features for every epoch")
+    parser.add_argument(
+        "--plot", action="store_true", help="whether to plot features for every epoch"
+    )
 
     # tensorboard logger
     parser.add_argument(
@@ -170,8 +169,7 @@ class Trainer:
         self.args = args
 
         # Set device for allocation of the tensor
-        self.device = torch.device(
-            "cuda" if torch.cuda.is_available() else "cpu")
[…]

### 2022-01-20 step1_KnownUnknownSep.py

@@ -59,9 +59,6 @@ def _do_epoch(
     """
     criterion = nn.CrossEntropyLoss()
     # Initialize center loss
-    
-    center_loss = CenterLoss(args.n_classes_known*4,
-                             256*args.n_classes_known, False)
     feature_extractor.train()
     obj_cls.train()
     rot_cls.train()
@@ -83,8 +80,7 @@ def _do_epoch(
         # Pass features to classifiers
         class_scores = obj_cls(original_features)
         # Here we have to concatenate tensors as suggested by the architecture
-        rotation_scores = rot_cls(
-            torch.cat([original_features, rotated_features], 1))
+        rotation_scores = rot_cls(torch.cat([original_features, rotated_features], 1))
 
         # Concatenation of the features
         features = torch.cat([original_features, rotated_features], 1)
@@ -100,8 +96,7 @@ def _do_epoch(
         loss.backward()
         for param in center_loss.parameters():
             # lr_cent is learning rate for center loss, e.g. lr_cent = 0.5
-            param.grad.data *= (args.lr_cent /
-                                (args.weight_cent * args.learning_rate))
+            param.grad.data *= args.lr_cent / (args.weight_cent * args.learning_rate)
 
         optimizer.step()
 
@@ -111,8 +106,7 @@ def _do_epoch(
 
         # Update counters
         correct_classes += torch.sum(class_prediction == class_label).item()
-        correct_rotations += torch.sum(rotation_prediction ==
-                                       rotated_label).item()
+        correct_rotations += torch.sum(rotation_prediction == rotated_label).item()
 
     acc_cls = correct_classes / len(source_loader.dataset)
     acc_rot = correct_rotations / len(source_loader.dataset)
@@ -142,7 +136,14 @@ def step1(
     for epoch in range(args.epochs_step1):
         print("Epoch: ", epoch)
         class_loss, acc_cls, rot_loss, acc_rot = _do_epoch(
-            args, feature_extractor, rot_cls, obj_cls, center_loss, source_loader, optimizer, device
+            args,
+            feature_extractor,
+            rot_cls,
+            obj_cls,
+            center_loss,
+            source_loader,
+            optimizer,
+            device,
         )
         print(
[…]

### 2022-01-20 main.py
Corrected loss function

@@ -182,7 +182,7 @@ class Trainer:
         # center_loss = CenterLoss(num_classes=self.ss_classes*self.n_classes, feat_dim=256*self.n_classes, use_gpu=True,device=self.device)
         # f second params=eat_dim=256*self.n_classes
 
-        self.center_loss = CenterLoss(4, 512 * 2, False)
+        self.center_loss = CenterLoss(4, 512 * 2, True)
 
         if args.load_weights:
             self.rot_classifier.load_state_dict(

### 2022-01-20 step1_KnownUnknownSep.py

@@ -25,7 +25,7 @@ def _do_epoch(
     source_loader: DataLoader,
     optimizer: torch.optim.Optimizer,
     device: torch.device,
-) -> Tuple[float, float, float, float]:
+) -> Tuple[float, float, float, float, float]:
     """
     Ideally we do an epoch and return all useful losses and accuracies.
 
@@ -88,10 +88,10 @@ def _do_epoch(
         # Now we can check the losses
         class_loss = criterion(class_scores, class_label)
         #  This needs CenterLoss to work better (see variation 3)
-        cent_loss = center_loss(features, rotated_label) * args.weight_cent
-        rot_loss = criterion(rotation_scores, rotated_label) + cent_loss
+        cent_loss = args.weight_cent * center_loss(features, rotated_label)
+        rot_loss = args.weight_RotTask_step1 * criterion(rotation_scores, rotated_label)
 
-        loss = class_loss + args.weight_RotTask_step1 * rot_loss
+        loss = class_loss + rot_loss + cent_loss
 
         loss.backward()
         for param in center_loss.parameters():
@@ -111,7 +111,7 @@ def _do_epoch(
     acc_cls = correct_classes / len(source_loader.dataset)
     acc_rot = correct_rotations / len(source_loader.dataset)
 
-    return class_loss, acc_cls, rot_loss, acc_rot
+    return class_loss, acc_cls, rot_loss, acc_rot, cent_loss
 
 
 def step1(
@@ -135,7 +135,7 @@ def step1(
 
     for epoch in range(args.epochs_step1):
         print("Epoch: ", epoch)
-        class_loss, acc_cls, rot_loss, acc_rot = _do_epoch(
+        class_loss, acc_cls, rot_loss, acc_rot, cent_loss = _do_epoch(
             args,
             feature_extractor,
             rot_cls,
@@ -146,8 +146,8 @@ def step1(
             device,
         )
         print(
-            "Class Loss %.4f, Class Accuracy %.4f,Rot Loss %.4f, Rot Accuracy %.4f"
-            % (class_loss, acc_cls, rot_loss, acc_rot)
+            "Class Loss %.4f, Class Accuracy %.4f,Rot Loss %.4f, Rot Accuracy %.4f, Center Loss: %.4f"
+            % (class_loss, acc_cls, rot_loss, acc_rot, cent_loss)
         )
         if epoch % 10 == 0:
             if not os.path.isdir("weights"):

### 2022-01-20 step2_SourceTargetAdapt.py
remove debug prints

@@ -164,11 +164,13 @@ def _do_epoch(
                     class_prediction == class_label
                 ).item()
 
+        """
         print("\n\ntotal classes known: " + str(total_classes_known))
         print("total classes unknown: " + str(total_classes_unknown))
         print("correct classes known: " + str(correct_classes_known))
         print("correct classes unknown: " + str(correct_classes_unknown))
-
+        """
+        
         # compute accuracies
         if total_classes_unknown == 0:
             print(

### 2022-01-20 main.py
Update main.py

@@ -120,7 +120,7 @@ def get_args():
         "--lr_cent", type=float, default=0.5, help="learning rate for center loss"
     )
     parser.add_argument(
-        "--weight_cent", type=float, default=1, help="weight for center loss"
+        "--weight_cent", type=float, default=0.01, help="weight for center loss"
     )
     parser.add_argument("--max_epoch", type=int, default=100)
     parser.add_argument("--stepsize", type=int, default=20)

### 2022-01-20 main.py
Updated step2 and added run for Product - Art (the worst result for standard version)

@@ -120,7 +120,7 @@ def get_args():
         "--lr_cent", type=float, default=0.5, help="learning rate for center loss"
     )
     parser.add_argument(
-        "--weight_cent", type=float, default=0.01, help="weight for center loss"
+        "--weight_cent", type=float, default=1, help="weight for center loss"
     )
     parser.add_argument("--max_epoch", type=int, default=100)
     parser.add_argument("--stepsize", type=int, default=20)
@@ -252,6 +252,7 @@ class Trainer:
                 self.args,
                 self.feature_extractor,
                 self.rot_cls,
+                self.center_loss,
                 self.target_loader_eval,
                 self.device,
             )
@@ -278,6 +279,7 @@ class Trainer:
                 self.feature_extractor,
                 self.rot_cls,
                 self.obj_cls,
+                self.center_loss,
                 self.source_loader,
                 self.target_loader_train,
                 self.target_loader_eval,

### 2022-01-20 step2_SourceTargetAdapt.py

@@ -150,7 +150,9 @@ def _do_epoch(
             # Update counters
             if class_label >= args.n_classes_known:
                 total_classes_unknown += 1
-                correct_classes_unknown += torch.sum(class_prediction == args.n_classes_known).item()
+                correct_classes_unknown += torch.sum(
+                    class_prediction == args.n_classes_known
+                ).item()
             else:
                 total_classes_known += 1
                 correct_classes_known += torch.sum(
@@ -177,6 +179,7 @@ def step2(
     feature_extractor,
     rot_cls,
     obj_cls,
+    center_loss,
     source_loader,
     target_loader_train,
     target_loader_eval,
@@ -205,11 +208,11 @@ def step2(
     device
         only passed through. CPU or GPU ?
     """
-
     optimizer, scheduler = get_optim_and_scheduler(
         feature_extractor,
         rot_cls,
         obj_cls,
+        center_loss,
         args.epochs_step2,
         args.learning_rate,
         args.train_all,

### 2022-01-20 main.py
Corrected main and added some evaluations

@@ -252,7 +252,6 @@ class Trainer:
                 self.args,
                 self.feature_extractor,
                 self.rot_cls,
-                self.center_loss,
                 self.target_loader_eval,
                 self.device,
             )

### 2022-01-21 Report/Paper_OpenSet.tex
Report - Completed ablation study

@@
 \usepackage{booktabs}
+\usepackage[export]{adjustbox}
+\usepackage{multirow}
 
@@
 
-Stage I of the simplified ROS method involves training both an object classifier and a rotation recognition task on data from the source domain, as shown on the left side of Figure \ref{fig:ROS}, where $D_s$ is the source domain dataset, $E$ is the encoder, $C_1$ is the object classifier and $R_1$ is the rotation classifier.
+Stage 1 of the simplified ROS method involves training both an object classifier and a rotation recognition task on data from the source domain, as shown on the left side of Figure \ref{fig:ROS}, where $D_s$ is the source domain dataset, $E$ is the encoder, $C_1$ is the object classifier and $R_1$ is the rotation classifier.
 The object prediction is based on the features of the original source samples, whereas the rotation prediction is based on the concatenated features of the original and rotated samples.
@@
 
-The precision of the normality score is then evaluated using the AUROC (Area Under Receiver Operating Characteristics curve) metric.
-The AUROC metric reduces analysis of the ROC curve to a single scalar value which can be used to compare the performance of classifiers \cite{Fawcett2006}.
-The higher the AUROC score the better the classifier overall, with scores $> 0.5$ showing an improvement over random guessing.
+The precision of the normality score is then evaluated using the AUC (area under receiver operating characteristics (ROC) curve) metric.
+The AUC metric reduces analysis of the ROC curve to a single scalar value which can be used to compare the performance of classifiers \cite{Fawcett2006}.
+The higher the AUC score the better the classifier overall, with scores $> 0.5$ showing an improvement over random guessing.
 
-If the AUROC is $> 0.5$ then the normality score can be used to conduct the known/unknown separation subject to a selected threshold, i.e.
+If the AUC is $> 0.5$ then the normality score can be used to conduct the known/unknown separation subject to a selected threshold, i.e.
 if the normality score is above the threshold the sample is considered as known and added to $D^{knw}_t$, otherwise it is considered as unknown and added to $D_t^{unk}$.
@@
 \subsection{Stage II - domain alignment}
+\label{sec:stage2}
 
-In stage II of the simplified ROS method the unknown dataset created from the target domain $D_t^{unk}$ is combined with the samples from the source domain $D_s$, with the unknown samples representing an additional `unknown' class.
+In stage 2 of the simplified ROS method the unknown dataset created from the target domain $D_t^{unk}$ is combined with the samples from the source domain $D_s$, with the unknown samples representing an additional `unknown' class.
 The object classifier $C_2$ is thus trained to recognise samples belonging to the unknown class.
@@
 \end{equation}
-where $\alpha_2$ is the weight assigned to the rotation recognition task of stage II.
+where $\alpha_2$ is the weight assigned to the rotation recognition task of stage 2.
 The value of $\alpha_2$ is also selected to provide the best performance, detailed further in Section \ref{sec:ablation}.
@@
 
-- the network used
+The proposed method was tested on the \textit{Office-Home} dataset \cite{OfficeHome}.
+This dataset consists of four separate domains for image classification: Art, Clipart, Product and Real World.
+An example of the difference between images in these domains is shown in Figure \ref{fig:domains}.
+Each domain included two sets of images, one when behaving as the source domain and another as the target, where the target domain included images from a number of categories that were non existant in the source domain set.
+
+\begin{figure}[!htbp]
+  \centering
+  \begin{adjustbox}{minipage=\linewidth,scale=0.8}
+  \begin{subfigure}[b]{0.45\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{Figures/Art_Radio.jpg}
+    \caption{Art}
+    \label{fig:short-a}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.45\columnwidth}
+\centering
+    \includegraphics[width=\linewidth]{Figures/Clipart_Radio.jpg}
+    \caption{Clipart}
+    \label{fig:short-b}
+  \end{subfigure}
+\vskip\baselineskip
+  \begin{subfigure}[b]{0.45\columnwidth}
+\centering
+    \includegraphics[width=\linewidth]{Figures/Product_Radio.jpg}
+    \caption{Product}
+    \label{fig:short-c}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.45\columnwidth}
+\centering
+    \includegraphics[width=\linewidth]{Figures/RealWorld_Radio.jpg}
+    \caption{Real World}
+    \label{fig:short-d}
+  \end{subfigure}
+\end{adjustbox}
+  \caption{Domains in the Office-Home dataset \cite{OfficeHome}.}
+  \label{fig:domains}
+\end{figure}
+
+The experiments were conducted using a ResNet18 convolutional neural network architecture, employing a learning rate of 0.001, a batch size of 128.
+Image data augmentation techniques were also emploted to improve performance of the model, these included random resized crop, color jitter and random grayscale.
 
@@
 
-- ablation study: hyperparameter tuning of weights and threshold value, include graphs or tables of values
+The simplified ROS method includes three hyperparameters that need to be tuned according to the network: the weight assigned to the rotation recognition tasks in stage 1 ($\alpha_1$); the threshold of normality score for considering a target sample as belong to a known category; and the weight assigned to the rotation recognition tasks in stage 2 ($\alpha_2$).
+The $\alpha_1$ parameter of stage 1 was tuned first.
+Figure \ref{fig:ClassAcc} shows the class accuracy of stage 1 when trained on the \textit{Art} source domain for a number of epochs and different $\alpha_1$ values, and Figure \ref{fig:RotAcc} shows the corresponding rotation recognition accuracy.
+As expected the accuracy of both increases with increasing number of epochs, however lower weights take much longer to converge for the rotation recognition tasks.
+Since the two classifiers are trained simultaneously a balance needs to be sought to reduce over-fitting of either task.
+
+\begin{figure}[!htb]
+  \centering
+   \includegraphics[width=0.95\linewidth]{Figures/ClassAcc.png}
+   \caption{Class accuracy during stage 1 training on the Art domain for various weights.}
+   \label{fig:ClassAcc}
+\end{figure}
+
+\begin{figure}[!htb]
+  \centering
+   \includegraphics[width=0.95\linewidth]{Figures/RotAcc.png}
+   \caption{Rotation recognition accuracy during stage 1 training on the Art domain for various weights.}
+   \label{fig:RotAcc}
+\end{figure}
+
+The AUC metric was then used to compare the performance of the various weights.
+The AUC value for the network with \textit{Art} as the source domain and \textit{Clipart} as the target domain is shown in Table \ref{tab:auc}.
+The highest AUC measured was 0.5578 for a weight of 10 at 40 epochs, therefore 10 was chosen at the values for $\alpha_1$ in stage 1.
+
+\begin{table}[!htb]
+  \centering
+  \begin{tabular}{@{}|l|ccccc|@{}}
+    \hline
+     & \multicolumn{5}{c|}{\textbf{Weight ( $\alpha_1$)}}\\
+ \textbf{Epoch} & 0.1 & 0.5 & 1 & 3 & 10 \\
+    \hline 
+    40 & 0.5293 & 0.4944 & 0.5245 & 0.5492 & 0.5578 \\
+   80 & 0.5203 & 0.4873 & 0.5312 & 0.5397 & 0.5548 \\
+    \hline
+  \end{tabular}
+  \caption{AUC for Art -- Clipart}
+  \label{tab:auc}
+\end{table}
+
+The next step involed tuning the threshold.
+The threshold should be chosen such that the number of samples recognised as known is similar to the number of samples that are expected to be recognised as known.
+Considering again the \textit{Art} as source and \textit{Clipart} as target domain combination as an example, the total number of samples in the \textit{Clipart} target domain is 4365, and 3064 of those samples share the same category as those in the \textit{Art} source domain.
+The model was thus evaluated with different thresholds and the number of samples identified as known analysed.
+Table \ref{tab:threshold} shows the results of the analysis on the \textit{Art}--\textit{Clipart} domain combination.
+A threshold of 0.75 results in the number of known samples being most similar to the expected number of known samples of 3064, and so 0.75 was chosen as the threshold for that combination.
+
+\begin{table}[!htb]
+  \centering
+  \begin{tabular}{@{}|cc|@{}}
+    \hline
+ \textbf{Threshold} & \textbf{Known Samples} \\
+    \hline 
+ 0.3 & 3778 \\
+ 0.5 & 3486 \\
+ 0.7 & 3123 \\
+ 0.75 & 3019 \\
+ 0.8 & 2872 \\
+    \hline
+  \end{tabular}
+  \caption{Samples recognised as known for various thresholds for the Art -- Clipart domain combination}
+  \label{tab:threshold}
+\end{table}
+
+The final step of the ablation study was to tune the stage 2 weight ($\alpha_2$).
+The evaluation metrics for stage 2 involve the harmonic mean between the accuracy of the known classes and the abiility of the classifier to recognize the unknown category, as discussed in \ref{sec:stage2}.
+The results of stage 2 for the \textit{Art}--\textit{Clipart} domain combination are shown in Table \ref{tab:tuneHOS}.
+The highest harmonic mean value is 0.4399, for a weight of 3 at 20 epochs.
+
+\begin{table}[!htb]
+  \centering
+  \begin{tabular}{@{}|ccccc|@{}}
+    \hline
+ \textbf{Weight ($\alpha_2$}) & \textbf{Epoch} & \textbf{OS$^*$} & \textbf{UNK} & \textbf{HOS} \\
+    \hline 
+ 0.01 & 20 & 0.3026 & 0.5778 & 0.3972 \\
+ & 40 & 0.3008 & 0.5743 & 0.3948 \\ \hline
+0.1 & 20 & 0.3091 & 0.5896 & 0.4056 \\
+ & 40 & 0.3257 & 0.5601 & 0.4119 \\\hline
+0.5 & 20 & 0.3280 & 0.5731 & 0.4172 \\
+ & 40 & 0.3404 & 0.5495 & 0.4204 \\\hline
+3 & 20 & 0.3542 & 0.5802 & 0.4399 \\
+ & 40 & 0.3690 & 0.5000 & 0.4246 \\\hline
+10 & 20 & 0.3114 & 0.6156 & 0.4136 \\
+ & 40 & 0.3367 & 0.5743 & 0.4246 \\
+    \hline
+  \end{tabular}
+  \caption{Stage 2 evaluation metrics for the Art -- Clipart domain combination}
+  \label{tab:tuneHOS}
+\end{table}
+
+Similar analyses were also conducted for the 11 other possible domain combinations, the results of which can be found in the supplementary material.
 

### 2022-01-21 Report/Paper_OpenSet.tex
Report - Variation descriptions

@@
 This study investigates the use of a simplified ROS method for object classification on the \textit{Office-Home} dataset \cite{OfficeHome}.
-Alternative self-supervised tasks \textcolor{red}{as well as the inclusion of center-loss} are also considered and their performance on the object classification task is evaluated.
+Alternative self-supervised tasks as well as the inclusion of center-loss are also considered and their performance on the object classification task is evaluated.
 
@@
 To solve the open-set domain adaptation problem a simplified version of the ROS method (Figure \ref{fig:ROS}) is used.
-This version uses a single-head rotation classifier and does not include the center-loss, \textcolor{red}{however the effect of the center-loss is evaluated subsequently as a variation to this method}.
-Alternative self-supervised tasks are also considered, including horizontal flipping, \textcolor{red}{vertical flipping} and through solving jigsaw puzzles.
+This version uses a single-head rotation classifier and does not include the center-loss, however the effect of the center-loss is evaluated subsequently as a variation to this method.
+Alternative self-supervised tasks are also considered, including horizontal flipping and through solving jigsaw puzzles.
 These variations are analyzed in Section \ref{sec:variations}.
@@
 An example of the difference between images in these domains is shown in Figure \ref{fig:domains}.
-Each domain included two sets of images, one when behaving as the source domain and another as the target, where the target domain included images from a number of categories that were non existant in the source domain set.
+For this experiment each domain included two sets of images, one when behaving as the source domain and another as the target.
+The dataset contained 65 classes in total.
+The classes were sorted alphabetically and the first 45 classes were treated as known and formed the list of images for the source domain, the remaining 20 were considered unknown and included in the list of images for the domain when behaving as the target domain.
 
@@
 
+The results for the simplified ROS model for each of the domain combinations is shown in Table \ref{tab:results}.
+
+\begin{table}[!htb]
+  \centering
+  \begin{tabular}{@{}|ll|ccc|@{}}
+    \hline
+\multicolumn{2}{|c}{\textbf{Domain}} & & & \\
+\textbf{Source} & \textbf{Target} & \textbf{OS$^*$} & \textbf{UNK} & \textbf{HOS} \\ \hline
+Art & Clipart & 35.42 & 58.02 & 43.99 \\
+& Product & & & \\
+ & Real World & & & \\ \hline
+Product & Clipart & & & \\
+& Art & & & \\
+& Real World & & & \\ \hline
+Real World & Clipart & & & \\
+ & Art & & & \\
+ & Product & & & \\ \hline
+Clipart & Real World & & & \\
+ & Art & & & \\
+& Product & & & \\
+    \hline
+  \end{tabular}
+  \caption{Accuracy (\%) for the simplified ROS model on the Office-Home dataset}
+  \label{tab:results}
+\end{table}
+
+- discussion
+
 %------------------------------------------------------------------------
@@
 \label{sec:variations}
+
+Two different variations to the simplified ROS method were also analysed.
+The first considered the use of alternative self-supervised tasks.
+The second considered the addition of the center-loss to the rotation recognition task.
+
+\subsection{Alternative self-supervised tasks}
+
+The simplified ROS method reported used rotation recognition as the self-supervised task, however many different self-supervised tasks are possible to be employed for use in open-set domain adaptation.
+This sudy investigated two alternative self-supervised tasks: hoizontal flipping; and solving jigsaw puzzles.
+
+\subsubsection*{Horizontal Flipping}
+
+Horizontal flipping is similar to image rotation however instead rotating the image it is flipped along its center y-axis, creating a mirror-image.
+Hoizontal flipping is shown in Figure \ref{fig:horiz}.
+
+\begin{figure}[!htb]
+  \centering
+   %\includegraphics[width=0.95\linewidth]{Figures/Jigsaw.png}
+   \caption{Horizontal flipping of an image.}
+   \label{fig:horiz}
+\end{figure}
+
+\subsubsection*{Jigsaw Puzzle}
+
+The self-supervised tasks of solving jigsaw puzzles involves being able to recognise an original image given its shuffled parts.
+The method involves first taking the orginal image, splitting the image into a number of sections, then creating a set of permutations with a different ordering of those sections.
+The method can be seen in Figure \ref{fig:jigsaw} as used by \cite{Carlucci2019}.
+The shuffled images (permutations) are then fed into the convolutional neural network to train the jigsaw classifier alongside the object classifier.
+\textcolor{red}{This study considered the images broken up into X number of sections, with X different permutations based on....}.
+
+\begin{figure*}[!htb]
+  \centering
+   \includegraphics[width=0.95\linewidth]{Figures/Jigsaw.png}
+   \caption{Jigsaw puzzle self-supervised task method \cite{Carlucci2019}.}
+   \label{fig:jigsaw}
+\end{figure*}
+
+\subsubsection*{Results}
+
+The harmonic mean results of the simplified ROS method employing different self-supervised tasks are shown in Table \ref{tab:selfs}.
+
+\begin{table}[!htb]
+\small
+  \centering
+  \begin{tabular}{@{}|ll|ccc|@{}}
+    \hline
+\multicolumn{2}{|c|}{\textbf{Domain}} & & \textbf{Horizontal} & \textbf{Jigsaw} \\
+\textbf{Source} & \textbf{Target} & \textbf{Rotation} & \textbf{Flipping} & \textbf{Puzzle} \\ \hline
+Art & Clipart & &  &  \\
+& Product & & & \\
+ & Real World & & & \\ \hline
+Product & Clipart & & & \\
+& Art & & & \\
+& Real World & & & \\ \hline
+Real World & Clipart & & & \\
+ & Art & & & \\
+ & Product & & & \\ \hline
+Clipart & Real World & & & \\
+ & Art & & & \\
+& Product & & & \\
+    \hline
+  \end{tabular}
+  \caption{Harmonic mean (\%) for the simplified ROS model with different self-supervised tasks on the Office-Home dataset}
+  \label{tab:selfs}
+\end{table}
+
+- discussion
+
+\subsection{Center-Loss}
 

### 2022-01-22 Report/Paper_OpenSet.tex

@@
 This study investigates the use of a simplified ROS method for object classification on the \textit{Office-Home} dataset \cite{OfficeHome}.
-Alternative self-supervised tasks as well as the inclusion of center-loss are also considered and their performance on the object classification task is evaluated.
+Alternative self-supervised tasks as well as the inclusion of center loss are also considered and their performance on the object classification task is evaluated.
 
@@
 The first stage separates samples in the target domain into known and unknown categories by training the model on a multi-rotation recognition task.
-The rotation recognition task includes the use of the center-loss to improve performance by learning a center of the features and minimizing the distances between features and their corresponding centers \cite{Wen2016}.
+The rotation recognition task includes the use of the center loss to improve performance by learning a center of the features and minimizing the distances between features and their corresponding centers \cite{Wen2016}.
 The second stage conducts domain alignment, training both semantic and rotation classifiers to classify known target samples.
@@
 To solve the open-set domain adaptation problem a simplified version of the ROS method (Figure \ref{fig:ROS}) is used.
-This version uses a single-head rotation classifier and does not include the center-loss, however the effect of the center-loss is evaluated subsequently as a variation to this method.
+This version uses a single-head rotation classifier and does not include the center loss, however the effect of the center loss is evaluated subsequently as a variation to this method.
 Alternative self-supervised tasks are also considered, including horizontal flipping and through solving jigsaw puzzles.
@@
 Art & Clipart & 35.42 & 58.02 & 43.99 \\
-& Product & & & \\
- & Real World & & & \\ \hline
-Product & Clipart & & & \\
-& Art & & & \\
+& Product & 42.27 & 46.21 & 44.15 \\
+ & Real World & 42.50 & 77.01 & 54.77 \\ \hline
+Product & Clipart & 38.05 & 55.94 & 45.29 \\
+& Art & 33.53 & 46.24 & 38.87 \\
 & Real World & & & \\ \hline
@@
 The first considered the use of alternative self-supervised tasks.
-The second considered the addition of the center-loss to the rotation recognition task.
+The second considered the addition of the center loss to the rotation recognition task.
 
@@
 
-\begin{figure}[!htb]
+\begin{figure}[!htbp]
   \centering
-   %\includegraphics[width=0.95\linewidth]{Figures/Jigsaw.png}
-   \caption{Horizontal flipping of an image.}
-   \label{fig:horiz}
+  %\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+  \begin{subfigure}[b]{0.4\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{Figures/FlipRaw.png}
+    \caption{Raw image}
+    \label{fig:short-a}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.4\columnwidth}
+\centering
+    \includegraphics[width=\linewidth]{Figures/FlipHoriz.png}
+    \caption{Horizontally flipped}
+    \label{fig:short-b}
+  \end{subfigure}
+%\end{adjustbox}
+  \caption{Horizontal flipping of an image, adapted from \cite{Xu22019}.}
+  \label{fig:centerloss}
 \end{figure}
@@
 
-\subsection{Center-Loss}
+\subsection{Center Loss}
+
+The center loss was introduced by Wen \etal \cite{Wen2016} as an additional objective function for enhancing the discriminative power of learned deep features.
+It involves learning the center of the deep features for each class, prioritizing features that are close to the center and adding a penalty to the distance between the deep features and their corresponding centers \cite{Wen2016}.
+The center loss function is optimised alongisde the soft max loss, with the two losses jointly supervised.
+A hyperparameter is introduced representing the weight of the center loss contribution, and is tuned to balance the two loss functions.The difference between the features learned by a classifier training with the soft max loss function on the MNIST dataset \cite{MNIST}, compared with the inclusion of the center loss during training is shown in Figure \ref{fig:centerloss}.
+The features learned with the inclusion of center loss can clearly be seen to provide greater discriminative power.
+
+\begin{figure}[!htbp]
+  \centering
+  %\begin{adjustbox}{minipage=\linewidth,scale=0.8}
+  \begin{subfigure}[b]{0.45\columnwidth}
+    \centering
+    \includegraphics[width=\linewidth]{Figures/SoftMaxLoss.png}
+    \caption{Soft Max Loss}
+    \label{fig:short-a}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.45\columnwidth}
+\centering
+    \includegraphics[width=\linewidth]{Figures/CenterLoss.png}
+    \caption{Center Loss}
+    \label{fig:short-b}
+  \end{subfigure}
+%\end{adjustbox}
+  \caption{Comparison of features learned when including the center loss on the MNIST dataset, adapted from \cite{Wen2016}.}
+  \label{fig:centerloss}
+\end{figure}
+
+An ablation study was performed to select the most appropriate weight of the center loss contribution.
 

### 2022-01-22 Report/Paper_OpenSet.tex
Center Loss in report

@@
 
-An ablation study was performed to select the most appropriate weight of the center loss contribution.
+The implementation of this loss affects only the first step of the model, so we have tried to understand the effect of center loss on the separation phase.
+
+An ablation study was performed to select the most appropriate weight ($\alpha_w$) of the center loss contribution.
+
+\subsection*{Results}
+
+Starting from the paper of Bucci \etal \cite{Bucci2020} we used the weights they tried in their research for Office-Home and Office31 datasets.
+Higher values give too much importance to center loss and the model is converging too much slow, so it is reasonable to test only values lower or equal to $0.01$.
+
+In the Table \ref{tab:center_loss} it is possible to see a comparison of the AUCROCs with and without the introduction of center loss with $\alpha_1 = 10$ trained for 40 epochs.
+Although we can reach better accuracy faster and get a little improvement in the model, but it is clear that more investigation is necessary to understand if in this case it is convenient to apply it.
+
+\begin{table}
+	\centering
+	\small
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		Domains & Metric & Standard & $\alpha_w = 0.001$ & $\alpha_w = 0.01$\\
+		\hline
+		\multirow{2}{*}{Art $\to$ Clipart}
+		& Aucroc & \textbf{0.5590} & 0.5486 & 0.5302\\ 
+		& Accuracy & 0.8988 & 0.9150 & 0.9150\\
+		\hline
+		\multirow{2}{*}{Product $\to$ Art}
+		& Aucroc & 0.4997 & \textbf{0.5077} & 0.5023\\ 
+		& Accuracy & 0.9513 & 0.9612 & 0.9631\\
+		\hline
+		\multirow{2}{*}{Art $\to$ RealWorld}
+		& Aucroc & 0.4956 & \textbf{0.5000} & 0.4967\\ 
+		& Accuracy & 0.8988 & 0.9128 & 0.9139\\
+		\hline
+	\end{tabular}
+	\caption{Comparison of center loss model with standard model}
+	\label{tab:center_loss}
+\end{table}
 

### 2022-01-22 Report/Paper_OpenSet.tex
Report - finished center loss section

--- 2022-01-22 Report/Paper_OpenSet.tex
@@
     \centering
-    \includegraphics[width=\linewidth]{Figures/FlipRaw.png}
+    \includegraphics[width=\linewidth]{Figures/FlipRaw.jpg}
     \caption{Raw image}
@@
   \end{subfigure}
+\hspace{0.01\textwidth}
   \begin{subfigure}[b]{0.4\columnwidth}
 \centering
-    \includegraphics[width=\linewidth]{Figures/FlipHoriz.png}
+    \includegraphics[width=\linewidth]{Figures/FlipHoriz.jpg}
     \caption{Horizontally flipped}
@@
 %\end{adjustbox}
-  \caption{Horizontal flipping of an image, adapted from \cite{Xu22019}.}
-  \label{fig:centerloss}
+  \caption{Horizontal flipping of an image, adapted from \cite{OfficeHome}.}
+  \label{fig:horiz}
 \end{figure}
@@
 
-\begin{figure*}[!htb]
+\begin{figure*}[!htbp]
   \centering
@@
 
-An ablation study was performed to select the most appropriate weight of the center loss contribution.
+The center loss has been implemented during the first step of the model, and used to understand the effect of this loss on the separation phase.
 
-- describe each of the variations
-- present results of the performance of the model and compare with the baseline for each of the variations
+\subsubsection*{Results}
+
+An ablation study was performed to select the most appropriate weight ($\alpha_w$) of the center loss contribution.
+The initial weights considered were based on those reported by Bucci \etal \cite{Bucci2020} in their research on the Office-Home \cite{OfficeHome} and Office31 datasets \cite{Office31}.
+High values of $\alpha_w$ were found to give too much importance to the center loss at the expense of the soft max loss, and the model converged extremely slowly.
+For this reason the results analysed here consider only weight values lower or equal to $0.01$.
+
+Table \ref{tab:center_loss} shows a comparison of the AUC values with and without the introduction of center loss, with $\alpha_1 = 10$ trained for 40 epochs.
+The inclusion of center loss was able to improve the accuracy for all domain configurations considered.
+It also improved the AUC metric for the second two domain configurations, however was detrimental in the first configuration.
+Due to the similarity of the results presented in \ref{tab:center_loss} the findings are inconclusive, and further investigations would be necessary to understand if the center loss could be used effectively in this scenario.
+
+\begin{table}
+	\centering
+	\small
+	\begin{tabular}{|l|c|c|c|c|}
+		\hline
+		 & & & \multicolumn{2}{c|}{\textbf{Weight  $\alpha_w$}} \\
+		Domains & Metric & Standard & 0.001 & 0.01\\
+		\hline
+		\multirow{2}{*}{Art $\to$ Clipart}
+		& AUC & \textbf{0.5590} & 0.5486 & 0.5302\\ 
+		& Accuracy & 0.8988 & 0.9150 & 0.9150\\
+		\hline
+		\multirow{2}{*}{Product $\to$ Art}
+		& AUC & 0.4997 & \textbf{0.5077} & 0.5023\\ 
+		& Accuracy & 0.9513 & 0.9612 & 0.9631\\
+		\hline
+		\multirow{2}{*}{Art $\to$ RealWorld}
+		& AUC & 0.4956 & \textbf{0.5000} & 0.4967\\ 
+		& Accuracy & 0.8988 & 0.9128 & 0.9139\\
+		\hline
+	\end{tabular}
+	\caption{Comparison of center loss model with standard model}
+	\label{tab:center_loss}
+\end{table}
 

### 2022-01-22 Report/Paper_OpenSet.tex
Report - finalised results

@@
 Domain adaptation can then be performed between the samples in the source domain and the samples recognized as known in the target domain.
-When applying domain adaptation to an open-set scenario (Open-Set Domain Adapatation or OSDA) the samples classified as unknown can be treated as a separate class and incorporated into the Closed-Set Domain Adaptation (CSDA) task~\cite{Pau2020}.
+When applying domain adaptation to an open-set scenario (Open-Set Domain Adaptation or OSDA) the samples classified as unknown can be treated as a separate class and incorporated into the Closed-Set Domain Adaptation (CSDA) task~\cite{Pau2020}.
 The self-supervised rotation task can also be used to reduce the domain shift during this step, using the Rotation-based Open Set (ROS) method developed by Bucci \etal \cite{Bucci2020}.
@@
 In this way the neural classifier learns features that are effective for the detection of anomalies.
-Sakurada and Yairi \cite{Sakurada2014} on the other hand make use of autoencoders with dimensionality reduction.
+Sakurada and Yairi \cite{Sakurada2014} on the other hand make use of auto-encoders with dimensionality reduction.
 This method assumes the data have correlations that can clearly separate normal and anomalous samples when reduced to a lower dimensional subspace.
@@
 The correct orientation of the object, however, is not an inherent property of an image, for example consider the pens in Figure \ref{fig:RotatedPens}.
-When analysing a rotated image of a pen it is not possible to infer the original rotation.
+When analyzing a rotated image of a pen it is not possible to infer the original rotation.
 The original image is therefore included in the rotation classifier and the relative rotation analysed instead.
 In training the rotation classifier the features of the original sample are concatenated with the features of the rotated sample.
-By including the original samples the network is also able to learn features that are more discriminative between class labels, focussing more on the shape of the object and less on the texture \cite{Bucci2020}, as shown in Figure \ref{fig:RotationFeatures}.
+By including the original samples the network is also able to learn features that are more discriminative between class labels, focusing more on the shape of the object and less on the texture \cite{Bucci2020}, as shown in Figure \ref{fig:RotationFeatures}.
 
@@
 In stage 2 of the simplified ROS method the unknown dataset created from the target domain $D_t^{unk}$ is combined with the samples from the source domain $D_s$, with the unknown samples representing an additional `unknown' class.
-The object classifier $C_2$ is thus trained to recognise samples belonging to the unknown class.
+The object classifier $C_2$ is thus trained to recognize samples belonging to the unknown class.
 Concurrently, the known target samples  $D^{knw}_t$ are used for the source-target adaptation by training the rotation recognition task $R_2$.
@@
 Once the classifiers have been trained the final evaluation can be completed.
-Three metrics are considered for the evalutation: the accuracy of the object classifier in correctly classifying objects of the known category $OS^*$; the accuracy of the object classifier in correctly identifying objects of the unknown category $UNK$; and the harmonic mean $HOS$ between the two accuracys $OS^*$ and $UNK$, as defined in \cite{Bucci2020}.
+Three metrics are considered for the evaluation: the accuracy of the object classifier in correctly classifying objects of the known category $OS^*$; the accuracy of the object classifier in correctly identifying objects of the unknown category $UNK$; and the harmonic mean $HOS$ between the two accuracies $OS^*$ and $UNK$, as defined in \cite{Bucci2020}.
 The harmonic mean is calculated as:
@@
 The experiments were conducted using a ResNet18 convolutional neural network architecture, employing a learning rate of 0.001, a batch size of 128.
-Image data augmentation techniques were also emploted to improve performance of the model, these included random resized crop, color jitter and random grayscale.
+Image data augmentation techniques were also employed to improve performance of the model, these included random resized crop, color jitter and random grayscale.
 
@@
 
-The simplified ROS method includes three hyperparameters that need to be tuned according to the network: the weight assigned to the rotation recognition tasks in stage 1 ($\alpha_1$); the threshold of normality score for considering a target sample as belong to a known category; and the weight assigned to the rotation recognition tasks in stage 2 ($\alpha_2$).
+The simplified ROS method includes three hyper-parameters that need to be tuned according to the network: the weight assigned to the rotation recognition tasks in stage 1 ($\alpha_1$); the threshold of normality score for considering a target sample as belong to a known category; and the weight assigned to the rotation recognition tasks in stage 2 ($\alpha_2$).
 The $\alpha_1$ parameter of stage 1 was tuned first.
@@
 
-The next step involed tuning the threshold.
-The threshold should be chosen such that the number of samples recognised as known is similar to the number of samples that are expected to be recognised as known.
+The next step involved tuning the threshold.
+The threshold should be chosen such that the number of samples recognized as known is similar to the number of samples that are expected to be recognized as known.
 Considering again the \textit{Art} as source and \textit{Clipart} as target domain combination as an example, the total number of samples in the \textit{Clipart} target domain is 4365, and 3064 of those samples share the same category as those in the \textit{Art} source domain.
@@
 The final step of the ablation study was to tune the stage 2 weight ($\alpha_2$).
-The evaluation metrics for stage 2 involve the harmonic mean between the accuracy of the known classes and the abiility of the classifier to recognize the unknown category, as discussed in \ref{sec:stage2}.
+The evaluation metrics for stage 2 involve the harmonic mean between the accuracy of the known classes and the ability of the classifier to recognize the unknown category, as discussed in \ref{sec:stage2}.
 The results of stage 2 for the \textit{Art}--\textit{Clipart} domain combination are shown in Table \ref{tab:tuneHOS}.
@@
 
-Similar analyses were also conducted for the 11 other possible domain combinations, the results of which can be found in the supplementary material.
+Similar analyses were also conducted for the 11 other possible domain combinations, the results of which can be found in the supplementary material\footnote{Additional results and the complete code is available at \url{https://github.com/DarthReca/AML-Project}.}.
 
@@
 The results for the simplified ROS model for each of the domain combinations is shown in Table \ref{tab:results}.
+The harmonic mean for each of the different domain combinations lies approximately between 40\% and 55\%.
+Different combinations performed better than others, however the results were sensitive to the input parameters.
+Depending on the application, prioritizing the accuracy of the categorization of the known class may prove beneficial and further training would be required.
+Results for the complete ROS method were published in \cite{Bucci2020} and reported a harmonic mean between approximately 55\% and 75\%.
+As expected the complete method performs better than the simplified method adopted in this study, however the simplified method could be employed in situations where a less complex approach is desired.
 
@@
 & Art & 33.53 & 46.24 & 38.87 \\
-& Real World & & & \\ \hline
-Real World & Clipart & & & \\
- & Art & & & \\
- & Product & & & \\ \hline
-Clipart & Real World & & & \\
- & Art & & & \\
-& Product & & & \\
+& Real World & 56.50 & 37.72 & 45.24 \\ \hline
+Real World & Clipart &43.87 & 50.76 & 47.07 \\
+ & Art & 46.86 & 44.54 & 45.67\\
+ & Product & 69.44 & 33.95 & 45.60 \\ \hline
+Clipart & Real World & 45.46 & 69.06 & 54.83\\
+ & Art & 33.71 & 58.14 & 42.67 \\
+& Product & 47.75 & 60.02 & 53.19 \\
     \hline
@@
 \end{table}
-
-- discussion
 
@@
 The simplified ROS method reported used rotation recognition as the self-supervised task, however many different self-supervised tasks are possible to be employed for use in open-set domain adaptation.
-This sudy investigated two alternative self-supervised tasks: hoizontal flipping; and solving jigsaw puzzles.
+This sudy investigated two alternative self-supervised tasks: horizontal flipping; and solving jigsaw puzzles.
 
@@
 Horizontal flipping is similar to image rotation however instead rotating the image it is flipped along its center y-axis, creating a mirror-image.
-Hoizontal flipping is shown in Figure \ref{fig:horiz}.
+Horizontal flipping is shown in Figure \ref{fig:horiz}.
 
@@
 
-The self-supervised tasks of solving jigsaw puzzles involves being able to recognise an original image given its shuffled parts.
-The method involves first taking the orginal image, splitting the image into a number of sections, then creating a set of permutations with a different ordering of those sections.
+The self-supervised tasks of solving jigsaw puzzles involves being able to recognize an original image given its shuffled parts.
+The method involves first taking the original image, splitting the image into a number of sections, then creating a set of permutations with a different ordering of those sections.
 The method can be seen in Figure \ref{fig:jigsaw} as used by \cite{Carlucci2019}.
 The shuffled images (permutations) are then fed into the convolutional neural network to train the jigsaw classifier alongside the object classifier.
-\textcolor{red}{This study considered the images broken up into X number of sections, with X different permutations based on....}.
+This study considered the images broken up into 9 sections, and then recombined based on a random permutation among 30 available permutations.
+For each image a shuffled one is generated and allocated an index.
+The convolutional neural network is then trained to predict its index.
+The Jigsaw puzzle task is formalized as a classification problem over recomposed images with the same dimension of the original one.
+In this way object recognition and patch reordering can share the same network backbone.
 
-\begin{figure*}[!htbp]
+\begin{figure}[!htbp]
   \centering
-   \includegraphics[width=0.95\linewidth]{Figures/Jigsaw.png}
-   \caption{Jigsaw puzzle self-supervised task method \cite{Carlucci2019}.}
+   \includegraphics[width=\linewidth]{Figures/Jigsaw2.png}
+   \caption{Jigsaw puzzle self-supervised task method, adapted from \cite{Carlucci2019}.}
    \label{fig:jigsaw}
-\end{figure*}
+\end{figure}
 
@@
 
-The harmonic mean results of the simplified ROS method employing different self-supervised tasks are shown in Table \ref{tab:selfs}.
+The harmonic mean results of the simplified ROS method employing different self-supervised tasks for a subset of domain configurations are shown in Table \ref{tab:selfs}.
+The first two configurations show the best performance using rotation recognition as the self-supervised task, however the third configuration performs best with horizontal flipping.
+It should be noted that in calculating these results the threshold parameter needed to be tuned independently for each self-supervised task, as this would have a significant effect on the results.
+The rotation recognition task seems to be the most robust method for conducting open-set domain adaption, in agreeance with the findings from Xu \etal \cite{Xu2019} and Gidaris \etal \cite{Gidaris2018}.
+As shown by this short study alternative self-supervised tasks may however perform better for some domain configurations.
 
@@
 \textbf{Source} & \textbf{Target} & \textbf{Rotation} & \textbf{Flipping} & \textbf{Puzzle} \\ \hline
-Art & Clipart & &  &  \\
-& Product & & & \\
- & Real World & & & \\ \hline
-Product & Clipart & & & \\
-& Art & & & \\
-& Real World & & & \\ \hline
-Real World & Clipart & & & \\
- & Art & & & \\
- & Product & & & \\ \hline
-Clipart & Real World & & & \\
- & Art & & & \\
-& Product & & & \\
+Art & Clipart & 43.99 & 35.11 & 18.64 \\
+Product & Art & 38.87 & 25.01 & 36.17\\
+Real World & Product  & 45.60 & 53.58 & 49.46\\
     \hline
@@
 
-- discussion
-
 \subsection{Center Loss}
@@
 It involves learning the center of the deep features for each class, prioritizing features that are close to the center and adding a penalty to the distance between the deep features and their corresponding centers \cite{Wen2016}.
-The center loss function is optimised alongisde the soft max loss, with the two losses jointly supervised.
-A hyperparameter is introduced representing the weight of the center loss contribution, and is tuned to balance the two loss functions.The difference between the features learned by a classifier training with the soft max loss function on the MNIST dataset \cite{MNIST}, compared with the inclusion of the center loss during training is shown in Figure \ref{fig:centerloss}.
+The center loss function is optimized alongside the soft max loss, with the two losses jointly supervised.
+A hyper-parameter is introduced representing the weight of the center loss contribution, and is tuned to balance the two loss functions.
+The difference between the features learned by a classifier training with the soft max loss function on the MNIST dataset \cite{MNIST}, compared with the inclusion of the center loss during training is shown in Figure \ref{fig:centerloss}.
 The features learned with the inclusion of center loss can clearly be seen to provide greater discriminative power.

### 2022-01-23 center_loss.py
Cleaned

@@ -1,3 +1,5 @@
+# CenterLoss by KaiyangZhou (see CENTER_LOSS_LICENSE)
+
 import torch
 import torch.nn as nn
 

### 2022-01-23 dataset.py

@@ -22,7 +22,6 @@ def _dataset_info(txt_labels) -> Tuple[List[str], List[int]]:
     return file_names, labels
 
 
-# It returns train_dataset
 class Dataset(data.Dataset):
     def __init__(
         self,
@@ -60,7 +59,6 @@ class Dataset(data.Dataset):
         return len(self.names)
 
 
-# It returns test_dataset
 class TestDataset(data.Dataset):
     def __init__(
         self,

### 2022-01-23 eval_target.py

@@ -9,7 +9,7 @@ import shutil
 
 from torch.utils.data.dataloader import DataLoader
 
-#### Implement the evaluation on the target for the known/unknown separation
+
 def evaluation(
     args: argparse.Namespace,
     feature_extractor: ResNet,
@@ -18,22 +18,20 @@ def evaluation(
     device: torch.device,
 ):
     """
-    Method is to be completed. It's supposed to do evaluation of the target domain:
-    if I can predict the orientation of the target image => image is from known category
-    results are returned in a file under the "new_txt_list" folder
+    Implement the evaluation on the target for the known/unknown separation
 
     Parameters
     ---------
-        args : data-type -> {source : str, target : str}
-            source and target fields contain the name of a class of images (such as "Clipart" or "RealWorld") (? maybe)
-        feature_extractor
-            only used for calling it's eval() method
-        rot_cls
-            stands for rotation classifier. Only used for calling it's eval() method
-        target_loader_eval : list<data-type> -> {data, class_l, data_rot, rot_l}
+        args : Namespace
+            All various arguments
+        feature_extractor: ResNet
+            feature extractor
+        rot_cls: Classifier
+            stands for rotation classifier.
+        target_loader_eval : Dataloader
             Is an iterable wrapping the dataset containing images of target domain and their labels. for each image contains: image, label for the image, rotated image, label for the rotated image
         device
-            CPU or GPU ?
+            CPU or GPU
     Returns
     -------
         rand : number
@@ -49,16 +47,9 @@ def evaluation(
         size=[len(target_loader_eval.dataset)], dtype=torch.int32
     )
 
-    # DEBUG VERSION
-    # normality_score = torch.empty(size=[512], dtype=torch.float32)
-    # ground_truth = torch.empty(size=[512], dtype=torch.int32)
-
     with torch.no_grad():
         # iterate over the target images to compute normality scores (i.e. how sure we are of the predicted rotation)
         for index, (data, class_l, _, _) in enumerate(target_loader_eval):
-            # DEBUG VERSION
-            # if index == 512:
-            #    break
 
             data, class_l = (
                 data.to(device),
@@ -119,9 +110,6 @@ def evaluation(
     number_of_unknown_samples = 0
     with torch.no_grad():
         for img_id, (_, class_l, _, _) in enumerate(target_loader_eval):
-            # DEBUG VERSION
-            # if img_id == 512:
-            #    break
             if normality_score[img_id] >= args.threshold:
                 # we consider the domain of the image as known
                 target_known.write(

### 2022-01-23 main.py

@@ -178,10 +178,6 @@ class Trainer:
         # Initiate rotation classifier with input_size=512*2 and 4 classes: [0, 90, 180, 270]
         self.rot_classifier = Classifier(512 * 2, 4)
 
-        # firs param =supervised * known
-        # center_loss = CenterLoss(num_classes=self.ss_classes*self.n_classes, feat_dim=256*self.n_classes, use_gpu=True,device=self.device)
-        # f second params=eat_dim=256*self.n_classes
-
         self.center_loss = CenterLoss(4, 512 * 2, True)
 
         if args.load_weights:
@@ -211,7 +207,6 @@ class Trainer:
         # Path to the file with the list of target images (from command line argument, default is Clipart)
         target_path_file = "txt_list/" + args.target + ".txt"
         # Create two data loaders for the target dataset, one for training and one for evaluation.
-        # (Probably this is a typo and the first one should be .get_train_dataloader as in step 2 below)
         self.target_loader_train = data_helper.get_val_dataloader(
             args, target_path_file
         )
@@ -224,10 +219,7 @@ class Trainer:
         )
 
     def do_training(self):
-        """
-        Runs the training
-
-        """
+        """Runs the training"""
 
         # Run step 1: train the object and rotation classifier
         if "step1" in self.args.steps:

### 2022-01-23 step1_KnownUnknownSep.py

@@ -7,10 +7,7 @@ from torch import nn
 from torch.utils.data import DataLoader
 from resnet import ResNet, Classifier
 import os
-import matplotlib
-from matplotlib import pyplot as plt
 from center_loss import CenterLoss
-import numpy as np
 
 
 # Implement Step1
@@ -159,27 +156,3 @@ def step1(
             torch.save(rot_cls.state_dict(), f"weights/rotation_classifier_{epoch}.pth")
 
         scheduler.step()
-
-
-def plot_features(features, labels, num_classes, epoch, prefix):
-    """Plot features on 2D plane.
-
-    Args:
-        features: (num_instances, num_features).
-        labels: (num_instances).
-    """
-    colors = ["C0", "C1", "C2", "C3", "C4", "C5", "C6", "C7", "C8", "C9"]
-    for label_idx in range(num_classes):
-        plt.scatter(
-            features[labels == label_idx, 0],
-            features[labels == label_idx, 1],
-            c=colors[label_idx],
-            s=1,
-        )
-    plt.legend(["0", "1", "2", "3", "4", "5", "6", "7", "8", "9"], loc="upper right")
-    dirname = osp.join(args.save_dir, prefix)
-    if not osp.exists(dirname):
-        os.mkdir(dirname)
-    save_name = osp.join(dirname, "epoch_" + str(epoch + 1) + ".png")
-    plt.savefig(save_name, bbox_inches="tight")
-    plt.close()

### 2022-01-23 step2_SourceTargetAdapt.py

@@ -1,26 +1,27 @@
+from center_loss import CenterLoss
+from resnet import Classifier, ResNet
 import torch
 from torch import nn
 from optimizer_helper import get_optim_and_scheduler
 from itertools import cycle
-import numpy as np
+from torch.utils.data import DataLoader
+from argparse import Namespace
 
 
 #### Implement Step2
-
-
 def _do_epoch(
-    args,
-    feature_extractor,
-    rot_cls,
-    obj_cls,
-    source_loader,
-    target_loader_train,
-    target_loader_eval,
-    optimizer,
-    device,
+    args: Namespace,
+    feature_extractor: ResNet,
+    rot_cls: Classifier,
+    obj_cls: Classifier,
+    source_loader: DataLoader,
+    target_loader_train: DataLoader,
+    target_loader_eval: DataLoader,
+    optimizer: torch.optim.Optimizer,
+    device: torch.device,
 ):
     """
-    Method is to be completed. It's supposed to predict orientation and class of each image,
+    It's supposed to predict orientation and class of each image,
     along with class and orientation loss and then do the final evaluation computing:
     OS: accuracy in recognizing known category
     UNK: accuracy in recognizing unknown category
@@ -28,24 +29,24 @@ def _do_epoch(
 
     Parameters
     ---------
-    args : data-type -> {epochs_step2 : int, weight_RotTask_step2 : float}
+    args : Namespace
         weight_RotTask_step2 is the alpha2 parameter (go to page 6 of project description)
     feature_extractor
-        only used for calling it's train() and eval() methods
-    rot_cls
-        stands for rotation classifier. only used for calling it's train() and eval() methods
-    obj_cls
-        stands for rotation classifier. only used for calling it's train() and eval() methods
-    source_loader : list<data-type> -> {data_source, class_l_source, _, _}
+        The features extractor
+    rot_cls: Classifier
+        stands for rotation classifier.
+    obj_cls: Classifier
+        stands for rotation classifier.
+    source_loader : Dataloader
         contains all the images of the source (data_source) and their assigned class (class_l_source)
-    target_loader_train: list<data-type> -> {data_target, _, data_target_rot, rot_l_target}
-        contains the target image, the rotated target image and (?) the label of the rotated target image (?)
-    target_loader_eval : list<data-type> -> {data_source, class_l_source, _, _}
+    target_loader_train: Dataloader
[…]

### 2022-01-23 data_helper.py
Cleaned

@@ -1,24 +1,7 @@
 import torch
-import torch.utils.data as data
 from torchvision import transforms
 
 from dataset import JigsawDataset, JigsawTestDataset, _dataset_info
-
-"""
-get_train_dataloader(args,txt_file) 
-Combines a dataset and a sampler, and provides an iterable over the given dataset. 
-Parameters:
-A dataset object (map style)
-args:
-path_dataset
-batch_size
-
-txt_file:
-(source_path_file/target_path_file)
-
-
-"""
-# Iteration ovetr test_dataset
 
 
 def get_train_dataloader(args, txt_file):
@@ -62,7 +45,8 @@ def get_val_dataloader(args, txt_file):
     img_tr = get_test_transformer(args)
 
     test_dataset = JigsawTestDataset(
-        names, labels, args.path_dataset, img_transformer=img_tr)
+        names, labels, args.path_dataset, img_transformer=img_tr
+    )
     loader = torch.utils.data.DataLoader(
         test_dataset,
         batch_size=1,
@@ -77,7 +61,6 @@ def get_val_dataloader(args, txt_file):
 
 # Used by get_train_dataloader()
 def get_train_transformers(args):
-    # Crop a random portion of image and resize it to a given size.
     """
     params:
     Size:image_size(h,w).

### 2022-01-23 dataset.py

@@ -1,17 +1,11 @@
-import enum
 import numpy as np
 import torch
 import torch.utils.data as data
-import torchvision
 import torchvision.transforms as transforms
 from PIL import Image
-import random
-from random import sample, random
 import torchvision.transforms.functional as TF
 import matplotlib.pyplot as plt
 from typing import List, Optional
-import torchvision.transforms.functional as F
-import os
 from itertools import product
 
 
@@ -30,6 +24,8 @@ def _dataset_info(txt_labels):
 
 
 class JigsawDataset(data.Dataset):
+    """This version works only with size 222, 222"""
+
     def __init__(
         self,
         names: List[str],
@@ -41,7 +37,7 @@ class JigsawDataset(data.Dataset):
         self.data_path = path_dataset
         self.names = names
         self.labels = labels
-        self.image_transformer = transforms.Resize(216)
+        self.image_transformer = img_transformer
 
         self.permutations = self.__retrieve_permutations(jig_classes)
 
@@ -79,6 +75,8 @@ class JigsawDataset(data.Dataset):
 
 
 class JigsawTestDataset(data.Dataset):
+    """This version works only with size 222, 222"""
+
     def __init__(
         self,
         names: List[str],
@@ -90,12 +88,12 @@ class JigsawTestDataset(data.Dataset):
         self.data_path = path_dataset
         self.names = names
         self.labels = labels
-        self.image_transformer = transforms.Resize(216)
+        self.image_transformer = img_transformer
 
         self.permutations = self.__retrieve_permutations(jig_classes)
 
     def __getitem__(self, index):
-          # Get and process an image
+        # Get and process an image
         image_path = self.data_path + "/" + self.names[index]
         img = TF.resize(Image.open(image_path).convert("RGB"), [222, 222])
 
@@ -127,19 +125,13 @@ class JigsawTestDataset(data.Dataset):
         return all_perm
 
 
-# sphinx_gallery_thumbnail_path = "../../gallery/assets/visualization_utils_thumbnail.png"
-
-
-# plt.rcParams["savefig.bbox"] = 'tight'
-
-
 def show(imgs):
     if not isinstance(imgs, list):
         imgs = [imgs]
     fix, axs = plt.subplots(ncols=len(imgs), squeeze=False)
     for i, img in enumerate(imgs):
         img = img.detach()
-        img = F.to_pil_image(img)
+        img = TF.to_pil_image(img)
[…]

### 2022-01-23 eval_target.py

@@ -18,27 +18,25 @@ def evaluation(
     device: torch.device,
 ):
     """
-    Method is to be completed. It's supposed to do evaluation of the target domain:
-    if I can predict the orientation of the target image => image is from known category
-    results are returned in a file under the "new_txt_list" folder
-
+    Implement the evaluation on the target for the known/unknown separation
     Parameters
     ---------
-        args : data-type -> {source : str, target : str}
-            source and target fields contain the name of a class of images (such as "Clipart" or "RealWorld") (? maybe)
-        feature_extractor
-            only used for calling it's eval() method
-        rot_cls
-            stands for rotation classifier. Only used for calling it's eval() method
-        target_loader_eval : list<data-type> -> {data, class_l, data_rot, rot_l}
+        args : Namespace
+            All various arguments
+        feature_extractor: ResNet
+            feature extractor
+        rot_cls: Classifier
+            stands for rotation classifier.
+        target_loader_eval : Dataloader
             Is an iterable wrapping the dataset containing images of target domain and their labels. for each image contains: image, label for the image, rotated image, label for the rotated image
         device
-            CPU or GPU ?
+            CPU or GPU
     Returns
     -------
         rand : number
             identifier of the file in which results of the evaluation will be stored
     """
+
     feature_extractor.eval()
     rot_cls.eval()
 
@@ -48,17 +46,9 @@ def evaluation(
     ground_truth = torch.empty(
         size=[len(target_loader_eval.dataset)], dtype=torch.int32
     )
-
-    # DEBUG VERSION
-    # normality_score = torch.empty(size=[512], dtype=torch.float32)
-    # ground_truth = torch.empty(size=[512], dtype=torch.int32)
-
     with torch.no_grad():
         # iterate over the target images to compute normality scores (i.e. how sure we are of the predicted rotation)
         for index, (data, class_l, _, _) in enumerate(target_loader_eval):
-            # DEBUG VERSION
-            # if index == 512:
-            #    break
 
             data, class_l = (
                 data.to(device),
@@ -119,9 +109,6 @@ def evaluation(
     number_of_unknown_samples = 0
     with torch.no_grad():
         for img_id, (_, class_l, _, _) in enumerate(target_loader_eval):
-            # DEBUG VERSION
-            # if img_id == 512:
-            #    break
             if normality_score[img_id] >= args.threshold:
                 # we consider the domain of the image as known
                 target_known.write(

### 2022-01-23 step1_KnownUnknownSep.py

@@ -73,12 +73,10 @@ def _do_epoch(
         # Pass features to classifiers
         class_scores = obj_cls(original_features)
         # Here we have to concatenate tensors as suggested by the architecture
-        rotation_scores = rot_cls(
-            torch.cat([original_features, rotated_features], 1))
+        rotation_scores = rot_cls(torch.cat([original_features, rotated_features], 1))
 
         # Now we can check the losses
         class_loss = criterion(class_scores, class_label)
-        # TODO: This needs CenterLoss to work better (see variation 3)
         rot_loss = criterion(rotation_scores, rotated_label)
 
         loss = class_loss + args.weight_RotTask_step1 * rot_loss
@@ -93,8 +91,7 @@ def _do_epoch(
 
         # Update counters
         correct_classes += torch.sum(class_prediction == class_label).item()
-        correct_rotations += torch.sum(rotation_prediction ==
-                                       rotated_label).item()
+        correct_rotations += torch.sum(rotation_prediction == rotated_label).item()
 
     acc_cls = correct_classes / len(source_loader.dataset)
     acc_rot = correct_rotations / len(source_loader.dataset)
@@ -132,11 +129,8 @@ def step1(
             if not os.path.isdir("weights"):
                 os.mkdir("weights")
             torch.save(
-                feature_extractor.state_dict(
-                ), f"weights/feature_extractor_{epoch}.pth"
+                feature_extractor.state_dict(), f"weights/feature_extractor_{epoch}.pth"
             )
-            torch.save(obj_cls.state_dict(),
-                       f"weights/object_classifier_{epoch}.pth")
-            torch.save(rot_cls.state_dict(),
-                       f"weights/rotation_classifier_{epoch}.pth")
+            torch.save(obj_cls.state_dict(), f"weights/object_classifier_{epoch}.pth")
+            torch.save(rot_cls.state_dict(), f"weights/rotation_classifier_{epoch}.pth")
         scheduler.step()

### 2022-01-23 step2_SourceTargetAdapt.py

@@ -1,51 +1,51 @@
+from resnet import Classifier, ResNet
 import torch
 from torch import nn
 from optimizer_helper import get_optim_and_scheduler
 from itertools import cycle
-import numpy as np
-
+from torch.utils.data import DataLoader
+from argparse import Namespace
 
 #### Implement Step2
 
 
 def _do_epoch(
-    args,
-    feature_extractor,
-    rot_cls,
-    obj_cls,
-    source_loader,
-    target_loader_train,
-    target_loader_eval,
-    optimizer,
-    device,
+    args: Namespace,
+    feature_extractor: ResNet,
+    rot_cls: Classifier,
+    obj_cls: Classifier,
+    source_loader: DataLoader,
+    target_loader_train: DataLoader,
+    target_loader_eval: DataLoader,
+    optimizer: torch.optim.Optimizer,
+    device: torch.device,
 ):
     """
-    Method is to be completed. It's supposed to predict orientation and class of each image,
+    It's supposed to predict orientation and class of each image,
     along with class and orientation loss and then do the final evaluation computing:
     OS: accuracy in recognizing known category
     UNK: accuracy in recognizing unknown category
     HOS: harmonic (~= average ) between the 2
-
     Parameters
     ---------
-    args : data-type -> {epochs_step2 : int, weight_RotTask_step2 : float}
+    args : Namespace
         weight_RotTask_step2 is the alpha2 parameter (go to page 6 of project description)
     feature_extractor
-        only used for calling it's train() and eval() methods
-    rot_cls
-        stands for rotation classifier. only used for calling it's train() and eval() methods
-    obj_cls
-        stands for rotation classifier. only used for calling it's train() and eval() methods
-    source_loader : list<data-type> -> {data_source, class_l_source, _, _}
+        The features extractor
+    rot_cls: Classifier
+        stands for rotation classifier.
+    obj_cls: Classifier
+        stands for rotation classifier.
+    source_loader : Dataloader
         contains all the images of the source (data_source) and their assigned class (class_l_source)
-    target_loader_train: list<data-type> -> {data_target, _, data_target_rot, rot_l_target}
-        contains the target image, the rotated target image and (?) the label of the rotated target image (?)
-    target_loader_eval : list<data-type> -> {data_source, class_l_source, _, _}
+    target_loader_train: Dataloader
+        contains the target image, the rotated target image and the label of the rotated target image
+    target_loader_eval : Dataloader
[…]

### 2022-01-23 center_loss.py
Moved results to a separate file, some cleaning

@@ -1,63 +1,0 @@
-import torch
-import torch.nn as nn
-
-
-class CenterLoss(nn.Module):
-    """Center loss.
-
-    Parameters
-    ----------
-    num_classes: int
-        number of classes.
-    feat_dim: int
-        feature dimension.
-
-    References
-    ----------
-    Wen et al. A Discriminative Feature Learning Approach for Deep Face Recognition. ECCV 2016.
-    """
-
-    def __init__(self, num_classes: int = 10, feat_dim: int = 2, use_gpu: bool = True):
-        super(CenterLoss, self).__init__()
-        self.num_classes = num_classes
-        self.feat_dim = feat_dim
-        self.use_gpu = use_gpu
-
-        if self.use_gpu:
-            self.centers = nn.Parameter(
-                torch.randn(self.num_classes, self.feat_dim).cuda()
-            )
-        else:
-            self.centers = nn.Parameter(torch.randn(self.num_classes, self.feat_dim))
-
-    def forward(self, x: torch.Tensor, labels: torch.Tensor):
-        """
-        Parameters
-        ----------
-        x: Tensor
-            feature matrix with shape (batch_size, feat_dim).
-        labels: Tensor
-            ground truth labels with shape (batch_size).
-        """
-        batch_size = x.size(0)
-        distmat = (
-            torch.pow(x, 2)
-            .sum(dim=1, keepdim=True)
-            .expand(batch_size, self.num_classes)
-            + torch.pow(self.centers, 2)
-            .sum(dim=1, keepdim=True)
-            .expand(self.num_classes, batch_size)
-            .t()
-        )
-        distmat.addmm_(1, -2, x, self.centers.t())
-
-        classes = torch.arange(self.num_classes).long()
-        if self.use_gpu:
-            classes = classes.cuda()
-        labels = labels.unsqueeze(1).expand(batch_size, self.num_classes)
-        mask = labels.eq(classes.expand(batch_size, self.num_classes))
-
-        dist = distmat * mask.float()
-        loss = dist.clamp(min=1e-12, max=1e12).sum() / batch_size
-
-        return loss

### 2022-01-23 data_helper.py

@@ -4,20 +4,6 @@ from torchvision import transforms
 
 from dataset import Dataset, TestDataset, _dataset_info
 
-"""
-get_train_dataloader(args,txt_file) 
-Combines a dataset and a sampler, and provides an iterable over the given dataset. 
-Parameters:
-A dataset object (map style)
-args:
-path_dataset
-batch_size
-
-txt_file:
-(source_path_file/target_path_file)
-
-
-"""
 # Iteration ovetr test_dataset
 def get_train_dataloader(args, txt_file):
     """

### 2022-01-23 eval_target.py

@@ -18,22 +18,19 @@ def evaluation(
     device: torch.device,
 ):
     """
-    Method is to be completed. It's supposed to do evaluation of the target domain:
-    if I can predict the orientation of the target image => image is from known category
-    results are returned in a file under the "new_txt_list" folder
-
+    Implement the evaluation on the target for the known/unknown separation
     Parameters
     ---------
-        args : data-type -> {source : str, target : str}
-            source and target fields contain the name of a class of images (such as "Clipart" or "RealWorld") (? maybe)
-        feature_extractor
-            only used for calling it's eval() method
-        rot_cls
-            stands for rotation classifier. Only used for calling it's eval() method
-        target_loader_eval : list<data-type> -> {data, class_l, data_rot, rot_l}
+        args : Namespace
+            All various arguments
+        feature_extractor: ResNet
+            feature extractor
+        rot_cls: Classifier
+            stands for rotation classifier.
+        target_loader_eval : Dataloader
             Is an iterable wrapping the dataset containing images of target domain and their labels. for each image contains: image, label for the image, rotated image, label for the rotated image
         device
-            CPU or GPU ?
+            CPU or GPU
     Returns
     -------
         rand : number
@@ -49,17 +46,9 @@ def evaluation(
         size=[len(target_loader_eval.dataset)], dtype=torch.int32
     )
 
-    # DEBUG VERSION
-    # normality_score = torch.empty(size=[512], dtype=torch.float32)
-    # ground_truth = torch.empty(size=[512], dtype=torch.int32)
-
     with torch.no_grad():
         # iterate over the target images to compute normality scores (i.e. how sure we are of the predicted rotation)
         for index, (data, class_l, _, _) in enumerate(target_loader_eval):
-            # DEBUG VERSION
-            # if index == 512:
-            #    break
-
             data, class_l = (
                 data.to(device),
                 class_l.to(device),
@@ -119,9 +108,6 @@ def evaluation(
     number_of_unknown_samples = 0
     with torch.no_grad():
         for img_id, (_, class_l, _, _) in enumerate(target_loader_eval):
-            # DEBUG VERSION
-            # if img_id == 512:
-            #    break
             if normality_score[img_id] >= args.threshold:
                 # we consider the domain of the image as known
                 target_known.write(

### 2022-01-23 step2_SourceTargetAdapt.py

@@ -1,51 +1,52 @@
+from resnet import Classifier, ResNet
 import torch
 from torch import nn
 from optimizer_helper import get_optim_and_scheduler
 from itertools import cycle
-import numpy as np
+from torch.utils.data import DataLoader
+from argparse import Namespace
 import os
 
 #### Implement Step2
 
 
 def _do_epoch(
-    args,
-    feature_extractor,
-    rot_cls,
-    obj_cls,
-    source_loader,
-    target_loader_train,
-    target_loader_eval,
-    optimizer,
-    device,
+    args: Namespace,
+    feature_extractor: ResNet,
+    rot_cls: Classifier,
+    obj_cls: Classifier,
+    source_loader: DataLoader,
+    target_loader_train: DataLoader,
+    target_loader_eval: DataLoader,
+    optimizer: torch.optim.Optimizer,
+    device: torch.device,
 ):
     """
-    Method is to be completed. It's supposed to predict orientation and class of each image,
+    It's supposed to predict orientation and class of each image,
     along with class and orientation loss and then do the final evaluation computing:
     OS: accuracy in recognizing known category
     UNK: accuracy in recognizing unknown category
     HOS: harmonic (~= average ) between the 2
-
     Parameters
     ---------
-    args : data-type -> {epochs_step2 : int, weight_RotTask_step2 : float}
+    args : Namespace
         weight_RotTask_step2 is the alpha2 parameter (go to page 6 of project description)
     feature_extractor
-        only used for calling it's train() and eval() methods
-    rot_cls
-        stands for rotation classifier. only used for calling it's train() and eval() methods
-    obj_cls
-        stands for rotation classifier. only used for calling it's train() and eval() methods
-    source_loader : list<data-type> -> {data_source, class_l_source, _, _}
+        The features extractor
+    rot_cls: Classifier
+        stands for rotation classifier.
+    obj_cls: Classifier
+        stands for rotation classifier.
+    source_loader : Dataloader
         contains all the images of the source (data_source) and their assigned class (class_l_source)
-    target_loader_train: list<data-type> -> {data_target, _, data_target_rot, rot_l_target}
-        contains the target image, the rotated target image and (?) the label of the rotated target image (?)
-    target_loader_eval : list<data-type> -> {data_source, class_l_source, _, _}
+    target_loader_train: Dataloader
+        contains the target image, the rotated target image and the label of the rotated target image
[…]

### 2022-01-23 Report/Paper_OpenSet.tex
Finished report

@@
 \begin{abstract}
-   - sentence describing the problem
- - sentence describing our proposed method
- - sentence summarising the results
- - sentence about the variations
- - sentence about the variation results
+Large amounts of data are available for use in computer vision research however the costs of labeling the data is high.
+Self-supervision techniques can be used to address this problem.
+This study investigates the use of self-supervision in an open-set domain adaptation scenario.
+A self-supervised tasks is trained alongside a classification task to separate known classes from unknown classes in the target domain.
+The technique investigated was a simplification of the Rotation-based Open Set (ROS) method, and was found to be less accurate but applicable to simplified scenarios.
+Various self-supervised tasks were also compared and the rotation recognition task was found to be the most robust compared to horizontal flipping or solving jigsaw puzzles.
+The inclusion of center loss during training was also investigated but the results were deemed inconclusive.
 \end{abstract}
@@
 
-\begin{table}
+\begin{table}[!htbp]
 	\centering
@@
 
-- summarise the results
-- add future recommendations
+This study investigated the use of a simplified ROS method for conducting open-set domain adaptation.
+The method was a simplified version of the ROS method reported in \cite{Bucci2020} by removing the center loss and using only a single-head rotation classifier.
+Results of the simplified version performed worse than the complete version when comparing the harmonic mean between the accuracy of the classification of known categories and the accuracy of identifying the unknown class.
+The simplified method however could be improved with further investigation into the effect of different input parameters, and could prove beneficial in situations where a less complex approach is desired.
+
+Variations to the simplified ROS method were also investigated, including the use of alternative self-supervised tasks and the addition of the center loss to the training of stage 1 of the model.
+Rotation recognition was found to be the most robust method for conducting self-supervision, however the alternative techniques could perform well in specific scenarios.
+The addition of the center loss to stage 1 in some instances was able to improve the performance of the model, and increase the pace at which appropriate features were identified.
+Further investigation into the utility of center loss is however recommended to better understand its application to open-set domain adaptation problems.
 

### 2022-01-23 Report/Paper_OpenSet.tex
Fixed typos

@@
 \begin{abstract}
-Large amounts of data are available for use in computer vision research however the costs of labeling the data is high.
+Large amounts of data are available for use in computer vision research however the cost of labeling the data is high.
 Self-supervision techniques can be used to address this problem.
 This study investigates the use of self-supervision in an open-set domain adaptation scenario.
-A self-supervised tasks is trained alongside a classification task to separate known classes from unknown classes in the target domain.
+A self-supervised task is trained alongside a classification task to separate known classes from unknown classes in the target domain.
 The technique investigated was a simplification of the Rotation-based Open Set (ROS) method, and was found to be less accurate but applicable to simplified scenarios.
-Various self-supervised tasks were also compared and the rotation recognition task was found to be the most robust compared to horizontal flipping or solving jigsaw puzzles.
-The inclusion of center loss during training was also investigated but the results were deemed inconclusive.
+Various self-supervised tasks were also compared and the rotation recognition task was found to be the most robust when compared to horizontal flipping or solving jigsaw puzzles.
+The inclusion of center loss during training was also investigated but the results were deemed inconclusive due to the similarity among the results.
 \end{abstract}
@@
   \end{tabular}
-  \caption{Samples recognised as known for various thresholds for the Art -- Clipart domain combination}
+  \caption{Samples recognized as known for various thresholds for the Art -- Clipart domain combination}
   \label{tab:threshold}
@@
 The simplified ROS method reported used rotation recognition as the self-supervised task, however many different self-supervised tasks are possible to be employed for use in open-set domain adaptation.
-This sudy investigated two alternative self-supervised tasks: horizontal flipping; and solving jigsaw puzzles.
+This study investigated two alternative self-supervised tasks: horizontal flipping; and solving jigsaw puzzles.
 

### 2022-01-23 data_helper.py
Cleaned

@@ -1,23 +1,8 @@
 import torch
-import torch.utils.data as data
 from torchvision import transforms
 
 from dataset import FlipDataset, TestFlipDataset, _dataset_info
 
-"""
-get_train_dataloader(args,txt_file) 
-Combines a dataset and a sampler, and provides an iterable over the given dataset. 
-Parameters:
-A dataset object (map style)
-args:
-path_dataset
-batch_size
-
-txt_file:
-(source_path_file/target_path_file)
-
-
-"""
 # Iteration ovetr test_dataset
 def get_train_dataloader(args, txt_file):
     """
@@ -40,8 +25,7 @@ def get_train_dataloader(args, txt_file):
     train_dataset = FlipDataset(
         name_train, labels_train, args.path_dataset, img_transformer=img_transformer
     )
-    
-    
+
     loader = torch.utils.data.DataLoader(
         train_dataset,
         batch_size=args.batch_size,
@@ -59,8 +43,10 @@ def get_val_dataloader(args, txt_file):
 
     names, labels = _dataset_info(txt_file)
     img_tr = get_test_transformer(args)
-    
-    test_dataset = TestFlipDataset(names, labels, args.path_dataset, img_transformer=img_tr)
+
+    test_dataset = TestFlipDataset(
+        names, labels, args.path_dataset, img_transformer=img_tr
+    )
     loader = torch.utils.data.DataLoader(
         test_dataset,
         batch_size=1,

### 2022-01-23 eval_target.py

@@ -18,22 +18,19 @@ def evaluation(
     device: torch.device,
 ):
     """
-    Method is to be completed. It's supposed to do evaluation of the target domain:
-    if I can predict the orientation of the target image => image is from known category
-    results are returned in a file under the "new_txt_list" folder
-
+    Implement the evaluation on the target for the known/unknown separation
     Parameters
     ---------
-        args : data-type -> {source : str, target : str}
-            source and target fields contain the name of a class of images (such as "Clipart" or "RealWorld") (? maybe)
-        feature_extractor
-            only used for calling it's eval() method
-        rot_cls
-            stands for rotation classifier. Only used for calling it's eval() method
-        target_loader_eval : list<data-type> -> {data, class_l, data_rot, rot_l}
+        args : Namespace
+            All various arguments
+        feature_extractor: ResNet
+            feature extractor
+        rot_cls: Classifier
+            stands for rotation classifier.
+        target_loader_eval : Dataloader
             Is an iterable wrapping the dataset containing images of target domain and their labels. for each image contains: image, label for the image, rotated image, label for the rotated image
         device
-            CPU or GPU ?
+            CPU or GPU
     Returns
     -------
         rand : number
@@ -49,36 +46,19 @@ def evaluation(
         size=[len(target_loader_eval.dataset)], dtype=torch.int32
     )
 
-    # DEBUG VERSION
-    # normality_score = torch.empty(size=[512], dtype=torch.float32)
-    # ground_truth = torch.empty(size=[512], dtype=torch.int32)
-
     with torch.no_grad():
         # iterate over the target images to compute normality scores (i.e. how sure we are of the predicted rotation)
         for index, (data, class_l, _, _) in enumerate(target_loader_eval):
-            # DEBUG VERSION
-            # if index == 512:
-            #    break
-
             data, class_l = (
                 data.to(device),
                 class_l.to(device),
             )
             original_features = feature_extractor(data)
 
-            """
-            entropy_losses = torch.zeros([4])
-            rotation_scores = torch.zeros([4, 4])
-            for i in range(1, 5):
-            
-                rotated_features = feature_extractor(
-                    torch.rot90(data, k=i, dims=[2, 3])
-                )
-            """
             entropy_losses = torch.zeros([2])
             rotation_scores = torch.zeros([2, 2])
             for i in range(2):
-                flipped = torch.fliplr(data) if i==1 else data
[…]

### 2022-01-23 step1_KnownUnknownSep.py

@@ -77,7 +77,6 @@ def _do_epoch(
 
         # Now we can check the losses
         class_loss = criterion(class_scores, class_label)
-        # TODO: This needs CenterLoss to work better (see variation 3)
         rot_loss = criterion(rotation_scores, rotated_label)
 
         loss = class_loss + args.weight_RotTask_step1 * rot_loss

### 2022-01-23 step2_SourceTargetAdapt.py

@@ -1,51 +1,53 @@
+from resnet import Classifier, ResNet
 import torch
 from torch import nn
 from optimizer_helper import get_optim_and_scheduler
 from itertools import cycle
-import numpy as np
+from torch.utils.data import DataLoader
+from argparse import Namespace
+import os
 
 
 #### Implement Step2
 
 
 def _do_epoch(
-    args,
-    feature_extractor,
-    rot_cls,
-    obj_cls,
-    source_loader,
-    target_loader_train,
-    target_loader_eval,
-    optimizer,
-    device,
+    args: Namespace,
+    feature_extractor: ResNet,
+    rot_cls: Classifier,
+    obj_cls: Classifier,
+    source_loader: DataLoader,
+    target_loader_train: DataLoader,
+    target_loader_eval: DataLoader,
+    optimizer: torch.optim.Optimizer,
+    device: torch.device,
 ):
     """
-    Method is to be completed. It's supposed to predict orientation and class of each image,
+    It's supposed to predict orientation and class of each image,
     along with class and orientation loss and then do the final evaluation computing:
     OS: accuracy in recognizing known category
     UNK: accuracy in recognizing unknown category
     HOS: harmonic (~= average ) between the 2
-
     Parameters
     ---------
-    args : data-type -> {epochs_step2 : int, weight_RotTask_step2 : float}
+    args : Namespace
         weight_RotTask_step2 is the alpha2 parameter (go to page 6 of project description)
     feature_extractor
-        only used for calling it's train() and eval() methods
-    rot_cls
-        stands for rotation classifier. only used for calling it's train() and eval() methods
-    obj_cls
-        stands for rotation classifier. only used for calling it's train() and eval() methods
-    source_loader : list<data-type> -> {data_source, class_l_source, _, _}
+        The features extractor
+    rot_cls: Classifier
+        stands for rotation classifier.
+    obj_cls: Classifier
+        stands for rotation classifier.
+    source_loader : Dataloader
         contains all the images of the source (data_source) and their assigned class (class_l_source)
-    target_loader_train: list<data-type> -> {data_target, _, data_target_rot, rot_l_target}
-        contains the target image, the rotated target image and (?) the label of the rotated target image (?)
-    target_loader_eval : list<data-type> -> {data_source, class_l_source, _, _}
+    target_loader_train: Dataloader
+        contains the target image, the rotated target image and the label of the rotated target image
[…]
